### 2024-11-18 paper/paper.qmd
model

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Fatimah Yunusa
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| include: false
#| warning: false
#| message: false
#install.packages("arrow")
#install.packages("tidyverse")
#install.packages("haven")
#install.packages("modelsummary")
#install.packages("kableExtra")
#install.packages("rstanarm")
#install.packages("bayesplot")
#install.packages("ggplot2")
#install.packages("brant")
#install.packages("pscl")

library(arrow)
library(tidyverse)
library(haven)
library(tidyverse)
library(palmerpenguins)
library(modelsummary)
library(kableExtra)
library(rstanarm)
library(bayesplot)
library(ggplot2)
library(brant)
library(pscl)

```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data
[@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an
entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

```{r}

```

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine
a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to
investigate... Background details and diagnostics are included in
[Appendix -@sec-model-details].

## Model set-up

# Results

Our results are summarized in

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what
your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Diagnostics

\newpage

# References

### 2024-11-18 paper/paper.tex
model

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={First author; Another author},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
\url{https://github.com/RohanAlexander/starter_folder}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Another author}
\date{November 17, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}

\section{Introduction}\label{introduction}

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. Section~\ref{sec-data}\ldots.

\section{Data}\label{sec-data}

\subsection{Overview}\label{overview}

We use the statistical programming language R (R Core Team 2023)\ldots.
Our data (Toronto Shelter \& Support Services 2024)\ldots. Following
Alexander (2023), we consider\ldots{}

Overview text

\subsection{Measurement}\label{measurement}

Some paragraphs about how we go from a phenomena in the world to an
entry in the dataset.

\subsection{Outcome variables}\label{outcome-variables}

Add graphs, tables and text. Use sub-sub-headings for each outcome
variable or update the subheading to be singular.

\subsection{Predictor variables}\label{predictor-variables}

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine
a few into one if they go together naturally.

\section{Model}\label{model}

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\subsection{Model set-up}\label{model-set-up}

Define \(y_i\) as the ordinal response variable representing the
perceived corruption in the office of the presidency. The covariates
include \(\text{education}_i\), \(\text{gender}_i\),
\(\text{urban/rural}_i\), and \(\text{age group}_i\).

The model can be expressed as:

{[} P(y\_i \leq k \textbar{} \eta\_i) =
\frac{\exp(\theta_k - \eta_i)}{1 + \exp(\theta_k - \eta_i)} {]}

where: - \(k\) is the ordinal category (e.g., ``None'', ``Some'',
``Most'', ``All''). -
\(\eta_i = \beta_0 + \beta_1 \, \text{education}_i + \beta_2 \, \text{gender}_i + \beta_3 \, \text{urban/rural}_i + \beta_4 \, \text{age group}_i\).
- \(\theta_k\) are the cut-points defining the thresholds between the
ordinal categories, such that
\(\theta_1 < \theta_2 < \dots < \theta_{k-1}\).

\subsubsection{Priors}\label{priors}

Assuming a Bayesian framework, the priors for the coefficients are
specified as:

{[} \beta\_j \sim \text{Normal}(0, 2.5) \quad \text{for all } j \in {1,
2, \dots, 4} {]} {[} \theta\_k \sim \text{Normal}(0, 5)
\quad \text{for all } k \in {1, 2, \dots, K-1} {]}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\subsubsection{Interpretation}\label{interpretation}

\begin{itemize}
\tightlist
\item
  \(\beta_j\): Coefficients representing the effect of the demographic
  variables on the perception of corruption.
\item
  \(\theta_k\): Thresholds dividing the ordinal categories.
\item
  \(y_i\): Ordered response variable modeled using the cumulative logit
  link function.
\end{itemize}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\subsubsection{Model justification}\label{model-justification}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\section{Results}\label{results}

Our results are summarized in

\section{Discussion}\label{discussion}

\subsection{First discussion point}\label{sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The
discussion is a chance to show off what you know and what you learnt
from all this.

\subsection{Second discussion point}\label{second-discussion-point}

Please don't use these as sub-heading labels - change them to be what
your point actually is.

\subsection{Third discussion point}\label{third-discussion-point}

\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}

Weaknesses and next steps should also be included.

\newpage

\appendix

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

\section{Additional data details}\label{additional-data-details}

\section{Model details}\label{sec-model-details}

\subsection{Diagnostics}\label{diagnostics}

\newpage

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-tellingstories}
Alexander, Rohan. 2023. \emph{Telling Stories with Data}. Chapman;
Hall/CRC. \url{https://tellingstorieswithdata.com/}.

\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-citeR}
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\bibitem[\citeproctext]{ref-shelter}
Toronto Shelter \& Support Services. 2024. \emph{Deaths of Shelter
Residents}.
\url{https://open.toronto.ca/dataset/deaths-of-shelter-residents/}.

\end{CSLReferences}

\end{document}

### 2024-11-18 scripts/03-clean_data.R

@@ -8,37 +8,86 @@
 # Any other information needed? [...UPDATE THIS...]
 
 #### Workspace setup ####
-library(tidyverse)
+install.packages("haven")    
+install.packages("dplyr")    
+install.packages("ggplot2")  
+install.packages("arrow")
+library(haven)
+library(dplyr)
+library(ggplot2)
+library(arrow)
 
-#### Clean data ####
-raw_data <- read_csv("inputs/data/plane_data.csv")
+nigeriasurvey <- read_sav("~/Downloads/nigeriasurvey.sav")
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
-  filter(wing_width_mm != "caw") |>
-  mutate(
-    flying_time_sec_first_timer = if_else(flying_time_sec_first_timer == "1,35",
-                                   "1.35",
-                                   flying_time_sec_first_timer)
-  ) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "490",
-                                 "49",
-                                 wing_width_mm)) |>
-  mutate(wing_width_mm = if_else(wing_width_mm == "6",
-                                 "60",
-                                 wing_width_mm)) |>
-  mutate(
-    wing_width_mm = as.numeric(wing_width_mm),
-    wing_length_mm = as.numeric(wing_length_mm),
-    flying_time_sec_first_timer = as.numeric(flying_time_sec_first_timer)
-  ) |>
-  rename(flying_time = flying_time_sec_first_timer,
-         width = wing_width_mm,
-         length = wing_length_mm
-         ) |> 
-  tidyr::drop_na()
+# Save the raw data as a Parquet file 
+write_parquet(nigeriasurvey, "data/01-raw_data/nigeriasurvey.parquet")
 
-#### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+# Reload the saved Parquet file to ensure it works
+nigeriasurvey <- read_parquet("data/01-raw_data/nigeriasurvey.parquet")
+
+
+# Select and clean relevant variables
+key_vars <- c("Q38A", "Q94", "Q101", "Q1", "URBRUR", "REGION")  # Include relevant columns
+cleaned_data <- nigeriasurvey %>%
+  select(all_of(key_vars)) %>%
+  filter(complete.cases(.))  # Remove rows with missing values in selected columns
+
[…]

### 2024-11-18 scripts/05-exploratory_data_analysis.R

@@ -9,29 +9,92 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
-
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
 
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
 
+#### Exploratory Data Analysis ####
 
+# Load necessary libraries
+install.packages(c("ggplot2", "dplyr"))
+library(ggplot2)
+library(dplyr)
+
+# Load the cleaned dataset
+cleaned_data <- read_parquet("data/02-analysis_data/fully_cleaned_nigeriasurvey.parquet")
+
+# Summary statistics of the cleaned dataset
+summary(cleaned_data)
+
+# Check for missing values across key variables
+sapply(cleaned_data, function(x) sum(is.na(x)))
+
+# Distribution of the perception of corruption
+ggplot(cleaned_data, aes(x = corruption_presidency)) +
+  geom_bar(fill = "steelblue") +
+  labs(title = "Distribution of Perception of Corruption in the Presidency",
+       x = "Perceived Corruption Level",
+       y = "Count")
+
+# Distribution of education levels
+ggplot(cleaned_data, aes(x = education)) +
+  geom_bar(fill = "darkgreen") +
+  labs(title = "Distribution of Education Levels",
+       x = "Education Level",
+       y = "Count") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Corruption perception by education
+ggplot(cleaned_data, aes(x = education, fill = corruption_presidency)) +
+  geom_bar(position = "fill") +
+  labs(title = "Perception of Corruption by Education Level",
+       x = "Education Level",
+       y = "Proportion") +
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+# Corruption perception by gender
+ggplot(cleaned_data, aes(x = gender, fill = corruption_presidency)) +
+  geom_bar(position = "fill") +
+  labs(title = "Perception of Corruption by Gender",
[…]

### 2024-11-24 paper/paper.qmd
model chage to OLR

@@
 #| message: false
-#install.packages("arrow")
-#install.packages("tidyverse")
-#install.packages("haven")
+
+#install.packages("rstanarm")
 #install.packages("modelsummary")
-#install.packages("kableExtra")
-#install.packages("rstanarm")
-#install.packages("bayesplot")
-#install.packages("ggplot2")
-#install.packages("brant")
-#install.packages("pscl")
-
-library(arrow)
-library(tidyverse)
-library(haven)
-library(tidyverse)
-library(palmerpenguins)
 library(modelsummary)
-library(kableExtra)
 library(rstanarm)
-library(bayesplot)
-library(ggplot2)
-library(brant)
-library(pscl)
 
@@
 
-```{r}
-
-```
-
 ## Predictor variables
@@
 
-Our results are summarized in
+Our results are summarized in @tbl-modelresults
 
@@
 #| message: false
+
+bayesian_model <- readRDS(file = here::here ("models/bayesian_model.rds"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Summary of the Ordinal Logistic regression model"
+#| warning: false
+
+# Install necessary packages if not already installed
+#install.packages("broom.mixed")
+#install.packages("kableExtra")
+
+# Load the packages
+library(broom.mixed)
+library(kableExtra)
+
+# Generate a tidy summary of your Bayesian model
+tidy_summary <- tidy(
+  bayesian_model, 
+  conf.int = TRUE,      # Include credible intervals
+  conf.level = 0.95     # Set confidence level to 95%
+)
+
+# Render the summary table as a nice HTML/LaTeX table
+tidy_summary %>%
+  kable(
+    caption = "Bayesian Model Summary with Credible Intervals",
+    digits = 2,             # Round numbers to 2 decimal places
+    col.names = c("Parameter", "Estimate", "Std. Error", "Lower 95% CI", "Upper 95% CI")  # Rename columns
+  ) %>%
+  kable_styling(
+    full_width = FALSE,
+    bootstrap_options = c("striped", "hover", "condensed")
+  )
 

### 2024-11-24 scripts/06-model_data.R

@@ -20,93 +20,49 @@
 #)
 
 
-#### Modeling: Ordinal Logistic Regression ####
-
 # Load necessary libraries
-install.packages(c("MASS", "broom", "ggplot2"))
-library(MASS)   # For ordinal regression
-library(broom)  # For tidy model outputs
-library(ggplot2)
+install.packages("MASS")
+install.packages("dplyr")
+install.packages("modelsummary")
+install.packges("rstanarm")
+linrary(rstanarm)
+library(MASS)
+library(dplyr)
+library(modelsummary)
 
-# Load the cleaned dataset
-#cleaned_data <- read_parquet("data/02-analysis_data/fully_cleaned_nigeriasurvey.parquet")
+# Read data 
 
-# Ensure variables are factors
-cleaned_data <- cleaned_data %>%
-  mutate(
-    gender = as.factor(gender),
-    urban_rural = as.factor(urban_rural),
-    education = as.factor(education),
-    age_group = as.factor(age_group),
-    corruption_presidency = as.ordered(corruption_presidency)  # Ensure outcome is ordered
-  )
+cleaned_data <- read_parquet("data/02-analysis_data/cleaned_nigeriasurvey.parquet")
+#### Model ####
+cleaned_data$corruption_presidency <- factor(
+  cleaned_data$corruption_presidency,
+  levels = c("None", "Some", "Most", "All"),
+  ordered = TRUE
+)
+
+# Verify the structure
+str(cleaned_data)
 
 # Fit the ordinal logistic regression model
-model <- polr(
-  corruption_presidency ~ education + gender + urban_rural + age_group, 
-  data = cleaned_data, 
-  method = "logistic"
+ordinal_model <- polr(
+  formula = corruption_presidency ~ education + gender + urban_rural + age_group,
+  data = cleaned_data,
+  method = "logistic"  # Logistic link function
 )
 
-# View model summary
-summary(model)
-
-# Tidy model output with coefficients and p-values
-model_results <- tidy(model, conf.int = TRUE)
-print(model_results)
-
-# Save model results to a CSV file
-write.csv(model_results, "models/model_results.csv", row.names = FALSE)
-
-# Calculate odds ratios for easier interpretation
-odds_ratios <- exp(coef(model))
-print(odds_ratios)
-
-# Save odds ratios to a CSV file
-write.csv(odds_ratios, "models/odds_ratios.csv")
-
[…]

### 2024-11-28 paper/paper.qmd
measurements, graphs and tables added

--- 2024-11-18 paper/paper.qmd
@@
 #| message: false
+#| label: setup
+#| 
+#install.packages("modelsummary")
+#install.packages("rstanarm")
+#install.packages("dplyr")
+#install.packages("here")
 #install.packages("arrow")
-#install.packages("tidyverse")
-#install.packages("haven")
-#install.packages("modelsummary")
-#install.packages("kableExtra")
-#install.packages("rstanarm")
-#install.packages("bayesplot")
-#install.packages("ggplot2")
-#install.packages("brant")
-#install.packages("pscl")
-
+library(modelsummary)
+library(rstanarm)
+library(dplyr)
+library(here)
 library(arrow)
-library(tidyverse)
-library(haven)
-library(tidyverse)
-library(palmerpenguins)
-library(modelsummary)
-library(kableExtra)
-library(rstanarm)
 library(bayesplot)
 library(ggplot2)
-library(brant)
-library(pscl)
+library(arrow)
+library(here)
 
+library(patchwork)
+
+# Load data
+cleaned_data <- read_parquet(here::here("data/02-analysis_data/cleaned_nigeriasurvey.parquet"))
+bayesian_model <- readRDS(file = here::here ("models/bayesian_model.rds"))
 ```
@@
 
+We use the statistical programming language R [@citeR]....
+
 # Data {#sec-data}
-
-## Overview
-
-We use the statistical programming language R [@citeR].... Our data
-[@shelter].... Following @tellingstories, we consider...
-
-Overview text
 
@@
 
-Some paragraphs about how we go from a phenomena in the world to an
-entry in the dataset.
+For this analysis, i use the Afrobarometer Rouund 9, Nigeria, 2023 survey.
+Afrobarometer conducts surveys that are nationally representative across African nations to capture public perceptions on topics like governance, democracy, and economic issues.
+The Nigerian Round 9 surveey dataset contains responses from 1,556 people and is refective of the diverse demographic statistics across gender, region, and residence type(urban or rural).
+The data is freely available on the Afrobarometer website[@afrobarometer2023] and was collected through a multi-stage, stratified sampling method.
+This is to ensure representativeness and enables analysis of different demographics and socioeconomic indicators.
+
+Our primary measurement task is to capture public opininon towards economic, political and socioeconomic issues and translate it into actionable intell.
+The Afrobarometer survey translates these real world perceptions into quantifiable data using survey instruments.The process begins with identifying relevant phenomena in the Nigerian socio-political and economic context, such as public attitudes toward democracy, demand for governance accountability, and perceived economic conditions.
+These phenomena are operationalized into survey questions that are clear, culturally sensitive, and tailored to elicit meaningful responses.
+
+For example:
+
+- Perceptions of Democracy: A phenomenon such as the demand for democracy is operationalized by questions asking respondents whether they prefer democracy over other forms of governance, and whether they believe Nigeria is a democratic nation.
+These questions are grounded in observable public discourse, historical trends, and policy outcomes.
+- Economic Prosperity: Attitudes toward economic conditions are measured by asking individuals to rate the current state of the economy and their own living standards.
+These subjective evaluations stem from tangible experiences like inflation, unemployment, or changes in public service delivery.
+
+Each survey question acts as a data proxy for these complex real-world dynamics, reducing them to quantifiable variables while maintaining their conceptual integrity.
+
+This dataset captures a unique moment in Nigeria's socio-political landscape, reflecting how citizens perceive democracy and governance in the context of ongoing economic and political challenges.
+Alternative datasets, such as Nigeria’s national statistics or World Bank survey data, could provide economic indicators but lack the granularity of Afrobarometer’s public opinion data.
+```{r}
+#| label: fig-urban-rural-distribution
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Figure 1: Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."
+
+# Plot: Urban vs Rural Respondent Distribution
+cleaned_data %>%
+  count(URBRUR) %>%
+  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Urban vs Rural Respondent Distribution",
+    x = "Respondent Location",
+    y = "Number of Respondents"
+  ) +
+  theme_minimal() +
+  scale_fill_manual(
+    values = c("Urban Residents" = "blue", "Rural Residents" = "gray")
+  ) +
+  guides(fill = "none")
+
+```
+
+```{r}
+#| label: fig-corruption-presidency
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Figure 2: Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."
+
+# Plot: Perceived Corruption in the Presidency
+cleaned_data %>%
+  count(corruption_presidency) %>%
+  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Perceived Corruption in the Presidency",
+    x = "Perception of Corruption",
+    y = "Number of Respondents"
+  ) +
+  theme_minimal() +
+  scale_fill_manual(
+    values = c("No Corruption" = "green", 
+               "Some Corruption" = "yellow", 
+               "High Corruption" = "red", 
+               "All Corrupt" = "purple")
+  ) +
+  guides(fill = "none")
+
+```
+```{r}
+#| label: fig-age-group-distribution
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Figure 3: Age Group Distribution. This bar chart displays the number of respondents in each age group."
+
+# Plot: Age Group Distribution
+cleaned_data %>%
+  count(age_group) %>%
+  ggplot(aes(x = age_group, y = n, fill = age_group)) +
+  geom_bar(stat = "identity") +
+  labs(
+    title = "Age Group Distribution",
+    x = "Age Group",
+    y = "Number of Respondents"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set3") +
+  guides(fill = "none")
+
+```
+```{r}
+#| label: fig-trust-political-institutions
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Figure 4: Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."
+
+library(haven)
+
+# Convert haven_labelled variables to appropriate types
+cleaned_data <- cleaned_data %>%
+  mutate(
+    Q38A = as.numeric(as.character(Q38A)), # Convert to numeric
+    Q94 = as.numeric(as.character(Q94)),   # Convert to numeric
+    Q101 = as.numeric(as.character(Q101)), # Convert to numeric if needed
+    URBRUR = as_factor(URBRUR),            # Convert to factor
+    corruption_presidency = as_factor(corruption_presidency), # Convert to factor
+    urban_rural = as_factor(urban_rural)   # Convert to factor
+  )
+
+# Plot: Trust in Political Institutions
+ggplot(cleaned_data, aes(x = Q38A)) +
+  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
+  labs(
+    title = "Trust in Political Institutions",
+    x = "Trust Level (1 = Low, 5 = High)",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+
+```
+```{r}
+#| label: fig-demand-democracy
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Figure 5: Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."
+
+# Plot: Demand for Democracy
+ggplot(cleaned_data, aes(x = Q94)) +
+  geom_histogram(binwidth = 1, fill = "orange", color = "black") +
+  labs(
+    title = "Demand for Democracy",
+    x = "Demand Level (1 = Low, 5 = High)",
+    y = "Frequency"
+  ) +
+  theme_minimal()
+
+```
+
+## Variables of Interest
 
@@
 variable or update the subheading to be singular.
-
-```{r}
-
-```
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+To investigate the relationship between demographic characteristics and different perceptions of corruption in Nigeria, we use a Bayesian Ordinal Logistic regression model.
 
-Here we briefly describe the Bayesian analysis model used to
-investigate... Background details and diagnostics are included in
+ Background details and diagnostics are included in
 [Appendix -@sec-model-details].
@@
 #| message: false
+
+bayesian_model <- readRDS(file = here::here ("models/bayesian_model.rds"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Summary of the Ordinal Logistic regression model"
+#| warning: false
+
+#install.packages("broom.mixed")
+#install.packages("kableExtra")
+
+library(broom.mixed)
+library(kableExtra)
+
+# Extract summary
+model_summary <- broom.mixed::tidy(bayesian_model)
+
+# Render as a table
+knitr::kable(
+  model_summary,
+  caption = "Summary of the Bayesian Model",
+  digits = 2
+) %>%
+  kableExtra::kable_styling()
 
@@
 
+## Posterior Predictive Check
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheck
+#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."
+
+# Load the Bayesian model
+bayesian_model <- readRDS(file = here::here("models/bayesian_model.rds"))
+
+# Posterior Predictive Check
+pp_check(bayesian_model) +
+  theme_classic() +
+  labs(
+    title = "Posterior Predictive Check",
+    x = "Observed Data",
+    y = "Density"
+  )
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-posteriorvsprior-education
+#| fig-cap: "Posterior vs Prior Comparison for Education Parameters."
+
+# Education Parameters
+education_params <- c(
+  "educationInformal schooling only",
+  "educationSome primary schooling",
+  "educationPrimary school completed",
+  "educationSome secondary schooling",
+  "educationSecondary school completed",
+  "educationPost-secondary qualifications",
+  "educationSome university",
+  "educationUniversity completed",
+  "educationPost-graduate"
+)
+
+posterior_vs_prior(bayesian_model, pars = education_params, group_by_parameter = TRUE) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  labs(
+    title = "Posterior vs Prior Comparison (Education Parameters)",
+    x = "Parameter Value",
+    y = "Density",
+    color = "Distribution"
+  )
+
+```
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-posteriorvsprior-demographic
+#| fig-cap: "Posterior vs Prior Comparison for Demographic Parameters."
+
+# Demographic Parameters
+demographic_params <- c(
+  "genderFemale",
+  "urban_ruralRural",
+  "age_group25-34",
+  "age_group35-44",
+  "age_group45-54",
+  "age_group55+"
+)
+
+posterior_vs_prior(bayesian_model, pars = demographic_params, group_by_parameter = TRUE) +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set2") +
+  theme(
+    legend.position = "bottom",
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  ) +
+  labs(
+    title = "Posterior vs Prior Comparison (Demographic Parameters)",
+    x = "Parameter Value",
+    y = "Density",
+    color = "Distribution"
+  )
+
+```
 ## Diagnostics
 
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-diagnostic-ppcheck
+#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."
+
+# Posterior Predictive Check
+pp_check(bayesian_model) +
+  theme_classic() +
+  labs(
+    title = "Posterior Predictive Check",
+    x = "Observed Data",
+    y = "Density"
+  )
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-diagnostic-traceplot
+#| fig-cap: "Trace plot for selected parameters in the Bayesian ordinal logistic regression model."
+
+# Trace Plot
+mcmc_trace(as.array(bayesian_model), pars = c("educationSome primary schooling", "urban_ruralRural")) +
+  theme_minimal() +
+  labs(
+    title = "Trace Plot for Selected Parameters",
+    x = "Iteration",
+    y = "Parameter Value"
+  )
+
+```
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-diagnostic-rhat
+#| fig-cap: "Rhat values for model convergence in the Bayesian ordinal logistic regression model."
+
+# Rhat Plot
+mcmc_rhat(rhat(bayesian_model)) +
+  theme_minimal() +
+  labs(
+    title = "Rhat Plot",
+    x = "Rhat Values",
+    y = "Parameters"
+  )
+
+```
+
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-diagnostic-ess
+#| fig-cap: "Effective sample size plot for parameters in the Bayesian ordinal logistic regression model."
+
+# Effective Sample Size Plot
+mcmc_neff(neff_ratio(bayesian_model)) +
+  theme_minimal() +
+  labs(
+    title = "Effective Sample Size Plot",
+    x = "Effective Sample Size Ratio",
+    y = "Parameters"
+  )
+
+```
 \newpage

### 2024-11-28 scripts/03-clean_data.R

@@ -85,9 +85,36 @@ cleaned_data <- cleaned_data %>%
 str(cleaned_data)
 summary(cleaned_data)
 
+cleaned_data <- cleaned_data %>%
+  mutate(
+    URBRUR = case_when(
+      URBRUR == 1 ~ "Urban Residents",
+      URBRUR == 2 ~ "Rural Residents",
+      TRUE ~ NA_character_ # Assign NA for unexpected values
+    )
+  )
+cleaned_data <- cleaned_data %>%
+  mutate(
+    urban_rural = case_when(
+      urban_rural == "Urban" ~ "Urban Residents",
+      urban_rural == "Rural" ~ "Rural Residents",
+      TRUE ~ NA_character_ # Assign NA for unexpected values
+    )
+  )
+
+cleaned_data <- cleaned_data %>%
+  mutate(
+    corruption_presidency = case_when(
+      corruption_presidency == "None" ~ "No Corruption",
+      corruption_presidency == "Some" ~ "Some Corruption",
+      corruption_presidency == "Most" ~ "High Corruption",
+      corruption_presidency == "All" ~ "All Corrupt",
+      TRUE ~ NA_character_ # Assign NA for unexpected values
+    )
+  )
+
 #### Save  cleaned data ####
 write_parquet(cleaned_data, "data/02-analysis_data/cleaned_nigeriasurvey.parquet")
 write.csv(cleaned_data, "data/02-analysis_data/cleaned_nigeriasurvey.csv", row.names = FALSE)
-
 
 

### 2024-11-28 scripts/06-model_data.R

@@ -43,13 +43,6 @@ cleaned_data$corruption_presidency <- factor(
 # Verify the structure
 str(cleaned_data)
 
-# Fit the ordinal logistic regression model
-ordinal_model <- polr(
-  formula = corruption_presidency ~ education + gender + urban_rural + age_group,
-  data = cleaned_data,
-  method = "logistic"  # Logistic link function
-)
-
 # Fit Bayesian ordinal logistic regression
 bayesian_model <- stan_polr(
   formula = corruption_presidency ~ education + gender + urban_rural + age_group,
@@ -58,10 +51,6 @@ bayesian_model <- stan_polr(
   prior_counts = dirichlet(alpha = 1),  # Dirichlet prior for ordinal response
   seed = 123  # For reproducibility
 )
-
-
-#### Save the Model ####
-saveRDS(ordinal_model, file = "models/ordinal_model.rds")
 
 
 # Save the model

### 2024-11-29 paper/paper.qmd
model specifications

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Perceptions of Corruption in Nigeria"
+subtitle: "Rural Nigerians and Less Educated  Groups Report Higher Corruption"
 author: 
   - Fatimah Yunusa
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-/tree/main"
 date: today
@@
 
-For this analysis, i use the Afrobarometer Rouund 9, Nigeria, 2023 survey.
-Afrobarometer conducts surveys that are nationally representative across African nations to capture public perceptions on topics like governance, democracy, and economic issues.
-The Nigerian Round 9 surveey dataset contains responses from 1,556 people and is refective of the diverse demographic statistics across gender, region, and residence type(urban or rural).
-The data is freely available on the Afrobarometer website[@afrobarometer2023] and was collected through a multi-stage, stratified sampling method.
-This is to ensure representativeness and enables analysis of different demographics and socioeconomic indicators.
+For this analysis, i use the Afrobarometer Rouund 9, Nigeria, 2023
+survey. Afrobarometer conducts surveys that are nationally
+representative across African nations to capture public perceptions on
+topics like governance, democracy, and economic issues. The Nigerian
+Round 9 surveey dataset contains responses from 1,556 people and is
+refective of the diverse demographic statistics across gender, region,
+and residence type(urban or rural). The data is freely available on the
+Afrobarometer website[@afrobarometer2023] and was collected through a
+multi-stage, stratified sampling method. This is to ensure
+representativeness and enables analysis of different demographics and
+socioeconomic indicators.
 
-Our primary measurement task is to capture public opininon towards economic, political and socioeconomic issues and translate it into actionable intell.
-The Afrobarometer survey translates these real world perceptions into quantifiable data using survey instruments.The process begins with identifying relevant phenomena in the Nigerian socio-political and economic context, such as public attitudes toward democracy, demand for governance accountability, and perceived economic conditions.
-These phenomena are operationalized into survey questions that are clear, culturally sensitive, and tailored to elicit meaningful responses.
+Our primary measurement task is to capture public opininon towards
+economic, political and socioeconomic issues and translate it into
+actionable intell. The Afrobarometer survey translates these real world
+perceptions into quantifiable data using survey instruments.The process
+begins with identifying relevant phenomena in the Nigerian
+socio-political and economic context, such as public attitudes toward
+democracy, demand for governance accountability, and perceived economic
+conditions. These phenomena are operationalized into survey questions
+that are clear, culturally sensitive, and tailored to elicit meaningful
+responses.
 
@@
 
-- Perceptions of Democracy: A phenomenon such as the demand for democracy is operationalized by questions asking respondents whether they prefer democracy over other forms of governance, and whether they believe Nigeria is a democratic nation.
-These questions are grounded in observable public discourse, historical trends, and policy outcomes.
-- Economic Prosperity: Attitudes toward economic conditions are measured by asking individuals to rate the current state of the economy and their own living standards.
-These subjective evaluations stem from tangible experiences like inflation, unemployment, or changes in public service delivery.
+-   Perceptions of Democracy: A phenomenon such as the demand for
+    democracy is operationalized by questions asking respondents whether
+    they prefer democracy over other forms of governance, and whether
+    they believe Nigeria is a democratic nation. These questions are
+    grounded in observable public discourse, historical trends, and
+    policy outcomes.
+-   Economic Prosperity: Attitudes toward economic conditions are
+    measured by asking individuals to rate the current state of the
+    economy and their own living standards. These subjective evaluations
+    stem from tangible experiences like inflation, unemployment, or
+    changes in public service delivery.
 
-Each survey question acts as a data proxy for these complex real-world dynamics, reducing them to quantifiable variables while maintaining their conceptual integrity.
+Each survey question acts as a data proxy for these complex real-world
+dynamics, reducing them to quantifiable variables while maintaining
+their conceptual integrity.
 
-This dataset captures a unique moment in Nigeria's socio-political landscape, reflecting how citizens perceive democracy and governance in the context of ongoing economic and political challenges.
-Alternative datasets, such as Nigeria’s national statistics or World Bank survey data, could provide economic indicators but lack the granularity of Afrobarometer’s public opinion data.
+This dataset captures a unique moment in Nigeria's socio-political
+landscape, reflecting how citizens perceive democracy and governance in
+the context of ongoing economic and political challenges. Alternative
+datasets, such as Nigeria’s national statistics or World Bank survey
+data, could provide economic indicators but lack the granularity of
+Afrobarometer’s public opinion data.
+
 ```{r}
@@
 ```
+
 ```{r}
@@
 
-# Model
+Background details and diagnostics are included in [Appendix
+-@sec-model-details].
 
-To investigate the relationship between demographic characteristics and different perceptions of corruption in Nigeria, we use a Bayesian Ordinal Logistic regression model.
-
- Background details and diagnostics are included in
-[Appendix -@sec-model-details].
+# Model {#sec-model}
 
@@
 
+A Bayesian ordinal logistic regression model is used to estimate the
+relationship between various demographic factors and perceptions of
+corruption in the presidency. Ordinal logistic regression is a
+statistical technique used for ordered categorical outcomes to predict
+the cumulative probability of being in a particular category or below,
+given a set of predictor variables.
+
+My model includes four independent demographic variables: `education`,
+`gender`, `urban_rural`, and `age_group`. The dependent variable is
+`corruption_presidency`, which has four ordered categories: "None,"
+"Some," "Most," and "All."
+
+The ordinal logistic regression model I used is: \begin{equation}
+\log\left(\frac{P(y_i \leq j)}{P(y_i > j)}\right) = \alpha_j - \left(\beta_1 \times \text{education} + \beta_2 \times \text{gender} + \beta_3 \times \text{urban rural} + \beta_4 \times \text{age group}\right)
+\end{equation}
+
+$$
+\begin{aligned}
+\beta_1 & \sim \mbox{Normal}(0, 2.5)\\
+\beta_2 & \sim \mbox{Normal}(0, 2.5)\\
+\beta_3 & \sim \mbox{Normal}(0, 2.5)\\
+\beta_4 & \sim \mbox{Normal}(0, 2.5)\\
+\alpha_j & \sim \mbox{Normal}(0, 2.5) \quad \text{for } j = 1, 2, 3\\
+\pi_{ij} & \sim \mbox{Dirichlet}(\alpha = 1)
+\end{aligned}
+$$ where:
+
+-   $y_i$ represents the ordinal outcome for respondent $i$, indicating
+    their perception of corruption in the presidency.
+
+-   $P(y_i \leq j)$ is the cumulative probability of respondent $i$
+    falling into category $j$ or below.
+
+-   $\alpha_j$ are the threshold parameters that define the boundaries
+    between the corruption categories.
+
+-   $\beta_1, \beta_2, \beta_3, \beta_4$ are the coefficients
+    corresponding to the predictors:
+
+    -   $\beta_1$: Education level of the respondent.
+    -   $\beta_2$: Gender of the respondent (male or female).
+    -   $\beta_3$: Urban or rural location of the respondent.
+    -   $\beta_4$: Age group of the respondent.
+
+-   $\pi_{ij}$ is the probability that respondent $i$ falls into
+    corruption category $j$.
+
+In this model, the priors reflect a belief that the predictors explain
+about 20% of the variability in the outcome, as defined by the
+$R^2(0.2)$ prior. The Normal priors with a mean of 0 and standard
+deviation of 2.5 for the coefficients and threshold parameters are
+relatively weakly informative, ensuring the data have a significant role
+in determining the posterior distributions.
+
+The threshold parameters ($\alpha_j$) separate the ordered categories of
+the outcome variable, while the Dirichlet prior for $\pi_{ij}$ assumes
+no strong prior preference for any specific corruption category.
+
+The use of these priors provides flexibility for the model while
+preventing overfitting. The posterior distributions for the coefficients
+and thresholds, along with diagnostic checks for model convergence and
+predictive accuracy, can be found in @sec-appendix.
+
+### Model Assumptions
+
+The model relies on the following assumptions:
+
+-   Proportional Odds: The relationship between the predictors and the
+    log-odds of being in a higher corruption category is constant across
+    thresholds.
+-   Ordinal Outcomes: The response categories are ordered, but the
+    distances between them are not quantitatively defined.
+-   Independence of observations: Responses from different individuals
+    are assumed to be independent.
+
+## Model Justification
+
+The Bayesian approach was chosen because of its flexibility in
+incorporating prior beliefs and its ability to provide real
+quantification for uncertainty for parameter estimates. An ordinal
+logistic regression model is appropriate because the outcome variable
+(perceived corruption) is inherently ordered.
+
+The predictors-education, gender, urban/rural location, and age group-
+were selected based on their theoretical relevance to perceptions of
+governmental corruption in Nigeria, as discussed in the data section.
+For example, urban and rural individuals may influence exposure to
+governance systems, while education might shape perceptions of systemic
+corruption.
+
+The modeling decisions align closely with the structure and
+characteristics of the dataset to ensure interpretability and relevance.
+Age was included as a categorical variable reflecting predefined groups,
+allowing the model to capture non-linear relationships between age and
+perceptions of corruption. Education was treated as a categorical
+variable to account for differences across distinct milestones, such as
+"Primary school completed" and "Post-graduate qualifications." Gender
+was modeled as a binary variable ("Male" or "Female") to reflect
+societal influences on corruption perceptions. Urban versus rural
+context was included as a binary variable to capture potential
+differences in exposure to governance and information access. While the
+dataset includes regional information, province effects were excluded to
+maintain focus on demographic factors and simplify the model. Finally,
+the ordinal logistic regression framework was chosen to respect the
+ordered nature of the outcome variable ("None," "Some," "Most," "All")
+without assuming equal distances between categories. These decisions
+ensure the model is both consistent with the data and well-suited to
+addressing the research question.
+
 # Results
 
-Our results are summarized in @tbl-modelresults
+## Corruption Perceptions Model
 
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-bayesian_model <- readRDS(file = here::here ("models/bayesian_model.rds"))
-```
+The analysis revealed distinct trends in Corruption perceptions in
+different demographics. Our results are summarized in @tbl-modelresults.
 
@@
   kableExtra::kable_styling()
+
+```
+## Predicted Probabilities
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: fig-predicted
+#| fig-cap: "Predicted probabilities of high corruption perceptions by key predictors."
+
+library(ggplot2)
+
+# Simulating or using your posterior data
+predicted_data <- data.frame(
+  Predictor = names(coef(bayesian_model)),
+  Estimate = coef(bayesian_model)
+)
+
+# Plot with adjusted x-axis labels
+ggplot(predicted_data, aes(x = Predictor, y = Estimate)) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Rotate and reduce size
+    axis.title.x = element_text(size = 10)
+  ) +
+  labs(
+    title = "Predicted Probabilities by Demographics",
+    x = "Predictor",
+    y = "Probability"
+  )
 
@@
 ```
+
 ## Diagnostics
@@
 ```
+
 \newpage

### 2024-11-29 paper/paper.qmd
readme updated & results section conclusion

@@
 ## Corruption Perceptions Model
-
-The analysis revealed distinct trends in Corruption perceptions in
-different demographics. Our results are summarized in @tbl-modelresults.
-
 ```{r}
@@
 ```
+
+The analysis revealed distinct trends in Corruption perceptions in
+different demographics.
+Our results are summarized in @tbl-modelresults.This presents the estimated coefficients and standard errors for each predictor included in the model.
+The dependent variable is the perception of corruption in the presidency, categorized into ordered levels.
+The table includes predictors such as education level, gender, urban or rural location, and agre group, which are modeled to explain variations in corruption perceptions.
+Each predictor's coefficient represents its effect on the log odds of perceiving corruption in the presidency at a specific level relative to lower levels, holding other variables constant.
+
+Higher education levels(e.g., university or post-graduate qualifications) arre associated with positive effects on corruption perceptions, indicating a greater likelihood of perceived higher levels of corruption.
+Begin female shows a small positive association with higher corruption perceptions.
+Residing in rural areas is negatively associated with corruption perceptions, suggesting lower perceptions of corruption compared to urban counterparts.
+Agegroups show minimal variation in their association with corruption perceptions, with no significant deviations observed among different age brackets.
+
 ## Predicted Probabilities
@@
 #| eval: true
-#| label: fig-predicted
+#| label: fig-predicted-probabilities
 #| fig-cap: "Predicted probabilities of high corruption perceptions by key predictors."
@@
 ```
+@fig-predicted-probabilities illustrates the predicted probabilities derived from the Bayesian ordinal logistic regression model for different demographic predictors influencing corruption perceptions in Nigeria.
+Each bar represents the estimated impact of a specific predictor on the likelihood of perceiving higher corruption levels in the presidency.
+
+Higher education levels consistently show positive probabilities, indicating that individuals with more advanced education levels are more likely to perceive higher corruption levels.
+Living in rural areas has a significantly negative probability, suggesting that rural residents are less likely to perceive high corruption compared to urban residents.
+Gender shows a moderate positive probability, with females slightly more likely to perceive higher corruption levels than males.
+There seems to be minimal variation observed across age groups, suggesting that age does not substantially influence perceptions of corruption.
+
+The results show that higher levels of education, particularly university completion and post-secondary qualifications, are associated with greater perceptions of corruption in the presidency.
+Urban residents demonstrate significantly higher perceived corruption levels compared to rural residents.
+Gender differences reveal that female respondents show slightly higher corruption perceptions, while age groups show minimal variation.
+These findings are shown in the regression estimates and predicted probabilities, as visualized in @fig-predicted-probabilities and summarized in @tbl-modelresults.
 

### 2024-11-29 paper/paper.qmd
readme spell check

@@
 #| label: setup
-#| 
+
 #install.packages("modelsummary")

### 2024-11-30 paper/paper.qmd
world bank refernce added

@@
 
+## Variables of Interest
 ```{r}
@@
 #| message: false
-#| fig.cap: "Figure 1: Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."
+#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."
 
@@
 
+@fig-urban-rural-distribution illustrates the distribution of survey
+respondents based on their residential location, categorized as urban or
+rural. From this, we see that the sample has more rural residents
+compared to urban residents. Specifically, the Afrobarometer survey for
+Nigeria, conducted in 2022, reports that approximately 53% of Nigeria's
+population resides in rural areas, this is is consistent with national
+demographic trends [@worldbank2022rural]. This rural-urban distribution
+is important for helping us understand the perspectives seen in the
+survey, since rural populations may have different challenges in
+governance and corruption compared to urban populations. The imbalance
+in representation shows that looking at geographical disparities when
+interpreting results from nationwide surveys is important.
+
 ```{r}
@@
 #| message: false
-#| fig.cap: "Figure 2: Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."
+#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."
 
@@
 
+@fig-corruption-presidency presents the distribution of respondents'
+perceptions of corruption within the Nigerian presidency. The variable 
+"Perceived Corruption in the Presidency" captures respondents' perceptions of 
+the extent of corruption within the Nigerian presidency and its officials. This 
+variable originates from Question 38A of the Afrobarometer survey, which asked:
+*"How many of the following people do you think are involved in corruption, or 
+haven’t you heard enough about them to say: the president and officials in his 
+office?"* [@Afrobarometer2022codebook] Respondents could choose from the following values:
+
+-   **0 (None)**: Indicates that the respondent perceives no corruption
+    in the office of the presidency.
+-   **1 (Some of them)**: Suggests that the respondent believes a few
+    individuals in the presidency are involved in corruption.
+-   **2 (Most of them)**: Reflects the perception that corruption is
+    prevalent among the majority of the presidency's officials.
+-   **3 (All of them)**: Suggests the respondent perceives widespread
+    corruption, implicating all officials in the presidency.
+-   **8 (Refused)**: Indicates the respondent declined to answer the
+    question.
+-   **9 (Don’t know/Haven’t heard enough)**: Suggests the respondent was
+    unsure or lacked sufficient knowledge to provide an answer.
+-   **-1 (Missing)**: Represents missing or unavailable responses.
+
+For the analysis, only the substantive responses (0-3) were considered,
+in order to help us look into perceptions of corruption within the presidency. 
+The high frequency of responses in the "High Corruption" and "Some
+Corruption" categories reflects persistent concerns about the integrity
+of key officials in Nigeria, aligning with broader findings on
+corruption in the region.@fig-corruption-presidency presents the distribution of 
+respondents' perceptions of corruption within the Nigerian presidency. Among
+these, the category "High corruption" is the most frequently reported,
+followed by "Some corruption". "All corrupt" ranks third, with "No
+Corruption" being the least chosen category which is no surprise given
+our data is in the context of Nigeria. These proportions show
+significant public concern about corruption within the presidency,
+consistent with broader trends in public concern abut corruption
+corruption within the presidency in Nigeria.
+
 ```{r}
@@
 #| message: false
-#| fig.cap: "Figure 3: Age Group Distribution. This bar chart displays the number of respondents in each age group."
+#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group."
 
@@
 ```
-
+@fig-age-group-distribution illustrates the distribution of survey respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54, and 55+.
+The data reveals that the 25-34 age group is the most represented, with over 500 respondents, followed by the 35-44 age group.
+The youngest cohort, aged 18-24, comprises approximately 300 respondents, while the older age groups (45-54 and 55+) are less represented in the dataset, with fewer than 200 respondents each.
+This distribution highlights a concentration of responses from younger demographics, particularly those aged 25-34, which may reflect broader societal trends such as population age structure or survey reach and accessibility.
 ```{r}
@@
 #| message: false
-#| fig.cap: "Figure 4: Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."
+#| fig.cap: "Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."
 
@@
 #| message: false
-#| fig.cap: "Figure 5: Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."
+#| fig.cap: "Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."
 
@@
 ```
-
-## Variables of Interest
 
@@
 ## Corruption Perceptions Model
+
 ```{r}
@@
 The analysis revealed distinct trends in Corruption perceptions in
-different demographics.
-Our results are summarized in @tbl-modelresults.This presents the estimated coefficients and standard errors for each predictor included in the model.
-The dependent variable is the perception of corruption in the presidency, categorized into ordered levels.
-The table includes predictors such as education level, gender, urban or rural location, and agre group, which are modeled to explain variations in corruption perceptions.
-Each predictor's coefficient represents its effect on the log odds of perceiving corruption in the presidency at a specific level relative to lower levels, holding other variables constant.
+different demographics. Our results are summarized in
+@tbl-modelresults.This presents the estimated coefficients and standard
+errors for each predictor included in the model. The dependent variable
+is the perception of corruption in the presidency, categorized into
+ordered levels. The table includes predictors such as education level,
+gender, urban or rural location, and agre group, which are modeled to
+explain variations in corruption perceptions. Each predictor's
+coefficient represents its effect on the log odds of perceiving
+corruption in the presidency at a specific level relative to lower
+levels, holding other variables constant.
 
-Higher education levels(e.g., university or post-graduate qualifications) arre associated with positive effects on corruption perceptions, indicating a greater likelihood of perceived higher levels of corruption.
-Begin female shows a small positive association with higher corruption perceptions.
-Residing in rural areas is negatively associated with corruption perceptions, suggesting lower perceptions of corruption compared to urban counterparts.
-Agegroups show minimal variation in their association with corruption perceptions, with no significant deviations observed among different age brackets.
+Higher education levels(e.g., university or post-graduate
+qualifications) arre associated with positive effects on corruption
+perceptions, indicating a greater likelihood of perceived higher levels
+of corruption. Begin female shows a small positive association with
+higher corruption perceptions. Residing in rural areas is negatively
+associated with corruption perceptions, suggesting lower perceptions of
+corruption compared to urban counterparts. Agegroups show minimal
+variation in their association with corruption perceptions, with no
+significant deviations observed among different age brackets.
 
@@
 ```
-@fig-predicted-probabilities illustrates the predicted probabilities derived from the Bayesian ordinal logistic regression model for different demographic predictors influencing corruption perceptions in Nigeria.
-Each bar represents the estimated impact of a specific predictor on the likelihood of perceiving higher corruption levels in the presidency.
 
-Higher education levels consistently show positive probabilities, indicating that individuals with more advanced education levels are more likely to perceive higher corruption levels.
-Living in rural areas has a significantly negative probability, suggesting that rural residents are less likely to perceive high corruption compared to urban residents.
-Gender shows a moderate positive probability, with females slightly more likely to perceive higher corruption levels than males.
-There seems to be minimal variation observed across age groups, suggesting that age does not substantially influence perceptions of corruption.
+@fig-predicted-probabilities illustrates the predicted probabilities
+derived from the Bayesian ordinal logistic regression model for
+different demographic predictors influencing corruption perceptions in
+Nigeria. Each bar represents the estimated impact of a specific
+predictor on the likelihood of perceiving higher corruption levels in
+the presidency.
 
-The results show that higher levels of education, particularly university completion and post-secondary qualifications, are associated with greater perceptions of corruption in the presidency.
-Urban residents demonstrate significantly higher perceived corruption levels compared to rural residents.
-Gender differences reveal that female respondents show slightly higher corruption perceptions, while age groups show minimal variation.
-These findings are shown in the regression estimates and predicted probabilities, as visualized in @fig-predicted-probabilities and summarized in @tbl-modelresults.
+Higher education levels consistently show positive probabilities,
+indicating that individuals with more advanced education levels are more
+likely to perceive higher corruption levels. Living in rural areas has a
+significantly negative probability, suggesting that rural residents are
+less likely to perceive high corruption compared to urban residents.
+Gender shows a moderate positive probability, with females slightly more
+likely to perceive higher corruption levels than males. There seems to
+be minimal variation observed across age groups, suggesting that age
+does not substantially influence perceptions of corruption.
+
+The results show that higher levels of education, particularly
+university completion and post-secondary qualifications, are associated
+with greater perceptions of corruption in the presidency. Urban
+residents demonstrate significantly higher perceived corruption levels
+compared to rural residents. Gender differences reveal that female
+respondents show slightly higher corruption perceptions, while age
+groups show minimal variation. These findings are shown in the
+regression estimates and predicted probabilities, as visualized in
+@fig-predicted-probabilities and summarized in @tbl-modelresults.
 

### 2024-12-01 paper/paper.qmd
packages referencing

@@
   - Fatimah Yunusa
-thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-/tree/main"
+thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
 date: today
@@
 format: pdf
+toc: true
 number-sections: true
@@
 #install.packages("arrow")
+#install.packages(tinytable)
 library(modelsummary)
@@
 library(here)
-
 library(patchwork)
@@
 
-We use the statistical programming language R [@citeR]....
-
 # Data {#sec-data}
@@
 
-For this analysis, i use the Afrobarometer Rouund 9, Nigeria, 2023
+For this analysis, i use the Afrobarometer Round 9, Nigeria, 2023
 survey. Afrobarometer conducts surveys that are nationally
@@
 topics like governance, democracy, and economic issues. The Nigerian
-Round 9 surveey dataset contains responses from 1,556 people and is
-refective of the diverse demographic statistics across gender, region,
+Round 9 survey dataset contains responses from 1,556 people and shows the diverse demographic statistics across gender, region,
 and residence type(urban or rural). The data is freely available on the
@@
 
-Our primary measurement task is to capture public opininon towards
+Our primary measurement task is to capture public opinion towards
 economic, political and socioeconomic issues and translate it into
-actionable intell. The Afrobarometer survey translates these real world
+actionable lintel. The Afrobarometer survey translates these real world
 perceptions into quantifiable data using survey instruments.The process
@@
 
+The data for this study was downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], a statistical programming language. The following packages were used:
+
+- **`modelsummary`** [@modelsummary]: Used to create well-formatted regression tables and summaries.
+- **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling using the Stan backend.
+- **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation, and summarization processes.
+- **`here`** [@here]: Simplified the organization of file paths, improving project reproducibility.
+- **`arrow`** [@arrow]: Enabled efficient handling of large datasets with fast reading and writing capabilities.
+- **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic checks and posterior predictive visualizations for Bayesian models.
+- **`ggplot2`** [@ggplot2]: Provided extensive tools for creating clear and impactful visualizations.
+- **`patchwork`** [@patchwork]: Combined multiple plots into cohesive, professional visuals.
+- **`knitr`** [@knitr]: Enabled dynamic report generation, integrating code, output, and text seamlessly.
+- **`kableExtra`** [@kableExtra]: Enhanced table styling and formatting for clean, professional presentations.
+- **`ggalt`** [@ggalt]: Allowed the creation of specialized plots, enhancing the depth of data visualizations.
+- **`haven`** [@haven]: Facilitated the import of `.sav` survey data from the Afrobarometer.
+- **`broom.mixed`** [@broommixed]: Streamlined the extraction and tidying of results from mixed models for easy analysis and visualization.
+- **`afrobarometer`** [@afrobarometer2023]: Served as the primary data source, providing valuable survey data for analysis.
+- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies.
+
+## Cleaned Data Overview 
+```{r}
+#| label: tbl-cleaned-data-preview
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| tbl-cap: "Preview of the Cleaned Dataset"
+
+#install.packages("knitr")
+#install.packages("kableExtra")
+library(knitr)
+library(kableExtra)
+
+# Create a preview of the cleaned dataset
+table_preview <- cleaned_data %>% 
+  select(-c(1:6)) %>%
+  head(6)
+
+# Generate a well-formatted table using kableExtra
+kable(
+  table_preview, 
+  caption = "Preview of the Cleaned Dataset"
+) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
+```
+
+@tbl-cleaned-data-preview represents the first six cleaned rows of the
+dataset, showing the important variables used in the analysis. The
+variables were constructed from specific survey questions in the
+Afrobarometer Round 9 Nigeria Survey [@afrobarometer2023], which
+captures several socioeconomic sentiments within the country.The column
+corruption_presidency captures perceptions of corruption within the
+office of the presidency, derived from responses to the question, “How
+many of the following people do you think are involved in corruption, or
+haven’t you heard enough about them to say: the president and officials
+in his office?” The variable education reflects respondents' highest
+level of education completed, gathered from the question, “What is the
+highest level of education you have completed?” The gender variable
+indicates the respondent's gender, collected through direct demographic
+inquiry. The column age_group categorizes respondents into age brackets
+based on the question, “How old are you?” The urban_rural variable
+distinguishes between urban and rural respondents, as recorded by
+interviewers based on the primary sampling unit (PSU) during data
+collection [@survey_manual_2022]. Lastly, region specifies the
+geographical region of each respondent, identified using a unique code
+for Nigerian states. This table not only demonstrates the diversity of
+the dataset but also highlights the breadth of demographic and
+governance-related variables included for analysis.
+
+```{r}
+#| label: tbl-summary-statistics
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| tbl-cap: "Detailed Summary Statistics of the Cleaned Dataset"
+
+library(dplyr)
+library(knitr)
+library(kableExtra)
+
+# Ensure the age_group column is a character for correct mapping
+cleaned_data <- cleaned_data %>%
+  mutate(age_group = as.character(age_group))
+
+# Function to calculate the mode (most frequent category)
+calculate_mode <- function(x) {
+  x <- na.omit(x)
+  unique_x <- unique(x)
+  unique_x[which.max(tabulate(match(x, unique_x)))]
+}
+
+# Adjust line breaks for proper rendering
+line_break <- ifelse(knitr::is_html_output(), "<br>", "\n")
+
+# Prepare the data for the transposed table
+transposed_summary <- tibble(
+  Statistic = c(
+    "Most Frequent Age Group", 
+    "Urban Percentage", 
+    "Male Percentage", 
+    "Corruption Counts", 
+    "Education Counts"
+  ),
+  Value = c(
+    calculate_mode(cleaned_data$age_group), 
+    paste0(round(mean(cleaned_data$urban_rural == "Urban Residents", na.rm = TRUE) * 100, 2), "%"),
+    paste0(round(mean(cleaned_data$gender == "Male", na.rm = TRUE) * 100, 2), "%"),
+    paste0(
+      "None: 61", line_break,
+      "Some: 574", line_break,
+      "High: 593", line_break,
+      "All: 328"
+    ),
+    paste0(
+      "Primary: 203", line_break,
+      "Secondary: 173", line_break,
+      "University: 102", line_break,
+      "Postgraduate: 07"
+    )
+  )
+)
+
+# Generate a formatted table
+kable(
+  transposed_summary, 
+  col.names = c("Statistic", "Value"),
+  caption = "Detailed Summary Statistics of the Cleaned Dataset (Transposed)",
+  escape = FALSE # Disables escaping for proper HTML/PDF formatting
+) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
+  column_spec(2, width = "20em") # Adjust width for better multiline display
+
+```
+The cleaned dataset used in this study is summarised in @tbl-summary-statistics, which provides key statistics to offer an overview of the dataset's structure and characteristics.
+The most frequent age group among respondents is identified, representing the predominant demographic in terms of age.
+The table also highlights the urban and male percentages, which indicate the proportion of urban residents (43.38%) and male respondents (49.68%) in the sample.
+
+Further, the table breaks down the perceptions of corruption into four categories—"None," "Some," "High," and "All"—with counts for each, offering insights into respondents' views on corruption in the presidency.
+Additionally, the table details the distribution of respondents across education levels, including categories such as "Primary," "Secondary," "University," and "Postgraduate." Together, these summary statistics provide a comprehensive snapshot of the dataset, enabling a clear understanding of its demographic and categorical variables.
+
 ## Variables of Interest
@@
 #| message: false
-#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas."
+#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas in Nigeria."
 
@@
 #| message: false
-#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency."
+#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency in Nigeria."
 
@@
 perceptions of corruption within the Nigerian presidency. The variable
-"Perceived Corruption in the Presidency" captures respondents' perceptions of 
-the extent of corruption within the Nigerian presidency and its officials. This 
-variable originates from Question 38A of the Afrobarometer survey, which asked:
-*"How many of the following people do you think are involved in corruption, or 
-haven’t you heard enough about them to say: the president and officials in his 
-office?"* [@Afrobarometer2022codebook] Respondents could choose from the following values:
+"Perceived Corruption in the Presidency" captures respondents'
+perceptions of the extent of corruption within the Nigerian presidency
+and its officials. This variable originates from Question 38A of the
+Afrobarometer survey, which asked: *"How many of the following people do
+you think are involved in corruption, or haven’t you heard enough about
+them to say: the president and officials in his office?"*
+[@Afrobarometer2022codebook] Respondents could choose from the following
+values:
 
@@
 For the analysis, only the substantive responses (0-3) were considered,
-in order to help us look into perceptions of corruption within the presidency. 
-The high frequency of responses in the "High Corruption" and "Some
-Corruption" categories reflects persistent concerns about the integrity
-of key officials in Nigeria, aligning with broader findings on
-corruption in the region.@fig-corruption-presidency presents the distribution of 
-respondents' perceptions of corruption within the Nigerian presidency. Among
-these, the category "High corruption" is the most frequently reported,
-followed by "Some corruption". "All corrupt" ranks third, with "No
-Corruption" being the least chosen category which is no surprise given
-our data is in the context of Nigeria. These proportions show
-significant public concern about corruption within the presidency,
-consistent with broader trends in public concern abut corruption
-corruption within the presidency in Nigeria.
+in order to help us look into perceptions of corruption within the
+presidency. The high frequency of responses in the "High Corruption" and
+"Some Corruption" categories reflects persistent concerns about the
+integrity of key officials in Nigeria, aligning with broader findings on
+corruption in the region. @fig-corruption-presidency presents the
+distribution of respondents' perceptions of corruption within the
+Nigerian presidency. Among these, the category "High corruption" is the
+most frequently reported, followed by "Some corruption". "All corrupt"
+ranks third, with "No Corruption" being the least chosen category which
+is no surprise given our data is in the context of Nigeria. These
+proportions show significant public concern about corruption within the
+presidency, consistent with broader trends in public concern abut
+corruption corruption within the presidency in Nigeria.
+
+```{r}
+#| label: fig-dumbbell-education
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Distribution of Education Levels in Nigeria"
+#install.packages("ggalt")
+library(ggalt)
+
+cleaned_data %>%
+  count(education) %>%
+  ggplot(aes(x = n, y = reorder(education, n))) +
+  geom_dumbbell(
+    aes(xend = 0, x = n), 
+    size = 3, colour = "darkblue", dot_guide = TRUE
+  ) +
+  theme_minimal() +
+  labs(
+    title = "Distribution of Education Levels in Nigeria",
+    x = "Number of Respondents", y = "Education Level"
+  )
+
+```
+
+@fig-dumbbell-education visually represents the educational attainment
+levels of respondents in the Afrobarometer survey for Nigeria. The data
+reflects responses to the question: *What is your highest level of
+education?*. The chart indicates that the most frequent reported level
+of education is "secondary school completed," followed by "primary
+school completed" and "no formal schooling". Fewer respondents reported
+having attained "post secondary qualifications," "university completed,"
+or "Post-graduate" education, shows the disparity in advanced
+educational attainment across the population. This distribution shows
+that basic education levels are more prevalent among respondents, which
+may influence their perceptions and responses in the broader survey.
+Including educational attainment is important in our analysis because it
+is an important socioeconomic factor.
 
@@
 #| message: false
-#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group."
+#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group in Nigeria."
 
@@
 ```
-@fig-age-group-distribution illustrates the distribution of survey respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54, and 55+.
-The data reveals that the 25-34 age group is the most represented, with over 500 respondents, followed by the 35-44 age group.
-The youngest cohort, aged 18-24, comprises approximately 300 respondents, while the older age groups (45-54 and 55+) are less represented in the dataset, with fewer than 200 respondents each.
-This distribution highlights a concentration of responses from younger demographics, particularly those aged 25-34, which may reflect broader societal trends such as population age structure or survey reach and accessibility.
-```{r}
-#| label: fig-trust-political-institutions
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "Distribution of Trust in Political Institutions. This histogram shows how respondents rated their trust in political institutions, from low to high trust."
 
-library(haven)
-
-# Convert haven_labelled variables to appropriate types
-cleaned_data <- cleaned_data %>%
-  mutate(
-    Q38A = as.numeric(as.character(Q38A)), # Convert to numeric
-    Q94 = as.numeric(as.character(Q94)),   # Convert to numeric
-    Q101 = as.numeric(as.character(Q101)), # Convert to numeric if needed
-    URBRUR = as_factor(URBRUR),            # Convert to factor
-    corruption_presidency = as_factor(corruption_presidency), # Convert to factor
-    urban_rural = as_factor(urban_rural)   # Convert to factor
-  )
-
-# Plot: Trust in Political Institutions
-ggplot(cleaned_data, aes(x = Q38A)) +
-  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
-  labs(
-    title = "Trust in Political Institutions",
-    x = "Trust Level (1 = Low, 5 = High)",
-    y = "Frequency"
-  ) +
-  theme_minimal()
-
-```
-
-```{r}
-#| label: fig-demand-democracy
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "Distribution of Demand for Democracy. This histogram illustrates respondents' levels of demand for democracy, with higher values reflecting stronger democratic preferences."
-
-# Plot: Demand for Democracy
-ggplot(cleaned_data, aes(x = Q94)) +
-  geom_histogram(binwidth = 1, fill = "orange", color = "black") +
-  labs(
-    title = "Demand for Democracy",
-    x = "Demand Level (1 = Low, 5 = High)",
-    y = "Frequency"
-  ) +
-  theme_minimal()
-
-```
-
-## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome
-variable or update the subheading to be singular.
-
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine
-a few into one if they go together naturally.
-
-Background details and diagnostics are included in [Appendix
--@sec-model-details].
+@fig-age-group-distribution illustrates the distribution of survey
+respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54,
+and 55+. The data reveals that the 25-34 age group is the most
+represented, with over 500 respondents, followed by the 35-44 age group.
+The youngest cohort, aged 18-24, comprises approximately 300
+respondents, while the older age groups (45-54 and 55+) are less
+represented in the dataset, with fewer than 200 respondents each. This
+distribution highlights a concentration of responses from younger
+demographics, particularly those aged 25-34, which may reflect broader
+societal trends such as population age structure or survey reach and
+accessibility.
 
@@
 and thresholds, along with diagnostic checks for model convergence and
-predictive accuracy, can be found in @sec-appendix.
+predictive accuracy, can be found in the Appendix.
 
@@
 The analysis revealed distinct trends in Corruption perceptions in
-different demographics. Our results are summarized in
-@tbl-modelresults.This presents the estimated coefficients and standard
+different demographics. Our results are summarized in @tbl-modelresults.This presents the estimated coefficients and standard
 errors for each predictor included in the model. The dependent variable

### 2024-12-01 scripts/00-simulate_data.R
simulated data created, tests run

@@ -10,10 +10,38 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
+library(readr)
 set.seed(200)
+
+#### Simulate data ####
+
+# Number of respondents
+n <- 1000
+
+simulated_afrobarometer <- data.frame(
+  respondent_id = 1:n,
+  age = sample(18:80, n, replace = TRUE),
+  gender = sample(c("Male", "Female"), n, replace = TRUE, prob = c(0.5, 0.5)),
+  education = sample(c("None", "Primary", "Secondary", "Tertiary"), n, replace = TRUE, prob = c(0.2, 0.3, 0.3, 0.2)),
+  income_level = sample(c("Low", "Middle", "High"), n, replace = TRUE, prob = c(0.5, 0.4, 0.1)),
+  trust_in_gov = sample(1:5, n, replace = TRUE, prob = c(0.1, 0.2, 0.3, 0.25, 0.15)), # 1 = No Trust, 5 = High Trust
+  corruption_perception = sample(1:5, n, replace = TRUE, prob = c(0.3, 0.3, 0.2, 0.15, 0.05)), # 1 = Very Corrupt, 5 = Not Corrupt
+  corruption_experience = rbinom(n, 1, prob = 0.3), # 0 = No, 1 = Yes
+  ethnic_group = sample(c("Hausa", "Yoruba", "Igbo", "Other"), n, replace = TRUE, prob = c(0.3, 0.3, 0.3, 0.1)),
+  region = sample(c("North", "South", "East", "West"), n, replace = TRUE),
+  urban_rural = sample(c("Urban", "Rural"), n, replace = TRUE, prob = c(0.6, 0.4)),
+  media_access = sample(1:5, n, replace = TRUE, prob = c(0.1, 0.2, 0.4, 0.2, 0.1)) # 1 = Low Access, 5 = High Access
+)
+
+# Adding derived variable: Perceived corruption risk based on perception and experience
+simulated_afrobarometer <-  simulated_afrobarometer %>%
+  mutate(
+    corruption_risk = ifelse(corruption_perception <= 2 | corruption_experience == 1, "High", "Low")
+  )
 
 
 #### Simulate data ####
 
 #### Save data ####
-write_csv(analysis_data, "data/00-simulated_data/simulated_data.csv")
+write_csv(simulated_afrobarometer, "data/00-simulated_data/simulated_afrobarometer.csv")

### 2024-12-01 scripts/01-test_simulated_data.R

@@ -7,82 +7,67 @@
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Any other information needed? Make sure you are in the `Nigeria_Democracy` rproj
 
 
 #### Workspace setup ####
+library(testthat)
+library(readr)
+library(dplyr)
 library(tidyverse)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_afrobarometer <- read_csv("data/00-simulated_data/simulated_afrobarometer.csv")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
-} else {
-  stop("Test Failed: The dataset could not be loaded.")
-}
-
+try({
+  simulated_afrobarometer <- read_csv("data/00-simulated_data/simulated_afrobarometer.csv")
+  # Check if the dataset is loaded successfully
+  if (exists("simulated_afrobarometer")) {
+    message("Test Passed: The dataset was successfully loaded.")
+  } else {
+    stop("Test Failed: The dataset could not be loaded.")
+  }
+}, silent = FALSE)
 
 #### Test data ####
 
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
-} else {
-  stop("Test Failed: The dataset does not have 151 rows.")
-}
-
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
-} else {
-  stop("Test Failed: The dataset does not have 3 columns.")
-}
-
-# Check if all values in the 'division' column are unique
-if (n_distinct(analysis_data$division) == nrow(analysis_data)) {
-  message("Test Passed: All values in 'division' are unique.")
-} else {
-  stop("Test Failed: The 'division' column contains duplicate values.")
-}
-
-# Check if the 'state' column contains only valid Australian state names
-valid_states <- c("New South Wales", "Victoria", "Queensland", "South Australia", 
-                  "Western Australia", "Tasmania", "Northern Territory", 
-                  "Australian Capital Territory")
-
-if (all(analysis_data$state %in% valid_states)) {
[…]

### 2024-12-01 scripts/04-test_analysis_data.R

@@ -9,61 +9,85 @@
 
 
 #### Workspace setup ####
-library(tidyverse)
-library(testthat)
+if (!requireNamespace("testthat", quietly = TRUE)) install.packages("testthat")
+if (!requireNamespace("validate", quietly = TRUE)) install.packages("validate")
+if (!requireNamespace("pointblank", quietly = TRUE)) install.packages("pointblank")
 
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
+library(testthat)
+library(validate)
+library(pointblank)
+library(dplyr)
+
+
+cleaned_data <- read_csv("data/02-analysis_data/cleaned_nigeriasurvey.csv")
 
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+
+
+### 1. TEST USING testthat
+test_that("Cleaned dataset has correct structure and data types", {
+  expect_true("corruption_presidency" %in% colnames(cleaned_data))
+  expect_true("education" %in% colnames(cleaned_data))
+  expect_true("gender" %in% colnames(cleaned_data))
+  expect_true("age_group" %in% colnames(cleaned_data))
+  expect_true("urban_rural" %in% colnames(cleaned_data))
+  
+  expect_s3_class(cleaned_data$corruption_presidency, "character")
+  expect_s3_class(cleaned_data$education, "character")
+  expect_s3_class(cleaned_data$gender, "character")
+  expect_s3_class(cleaned_data$age_group, "character")
+  expect_s3_class(cleaned_data$urban_rural, "character")
+}) 
+
+test_that("Cleaned dataset has no missing values in key columns", {
+  expect_true(all(!is.na(cleaned_data$corruption_presidency)))
+  expect_true(all(!is.na(cleaned_data$education)))
+  expect_true(all(!is.na(cleaned_data$gender)))
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+test_that("No unexpected values in categorical variables", {
+  expect_setequal(unique(cleaned_data$gender), c("Male", "Female"))
+  expect_setequal(unique(cleaned_data$urban_rural), c("Urban Residents", "Rural Residents"))
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
[…]

### 2024-12-02 paper/paper.qmd
corruption vs. variables ploted

@@
 
+## Combined variables of interest?
+
+```{r}
+#| label: fig-variables-of-interest
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "combined variables of interest"
+
+library(patchwork)
+
+# Create individual plots
+urban_plot <- cleaned_data %>%
+  count(URBRUR) %>%
+  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  labs(title = "Urban vs Rural", x = "Location", y = "Count")
+
+corruption_plot <- cleaned_data %>%
+  count(corruption_presidency) %>%
+  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  labs(title = "Corruption Perception", x = "Perception", y = "Count")
+
+education_plot <- cleaned_data %>%
+  count(education) %>%
+  ggplot(aes(x = n, y = reorder(education, n))) +
+  geom_col(fill = "darkblue") +
+  theme_minimal() +
+  labs(title = "Education Level", x = "Count", y = "Education")
+
+age_plot <- cleaned_data %>%
+  count(age_group) %>%
+  ggplot(aes(x = age_group, y = n, fill = age_group)) +
+  geom_bar(stat = "identity") +
+  theme_minimal() +
+  labs(title = "Age Distribution", x = "Age Group", y = "Count")
+
+# Combine plots
+urban_plot + corruption_plot + education_plot + age_plot +
+  plot_layout(ncol = 2)
+
+```
+
+```{r}
+#| label: fig-variables-of-interest-heatmap
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "combined variables of interest"
+
+#install.packages("tidyr")
+library(tidyr)
+# Combine data for heatmap
+heatmap_data <- cleaned_data %>%
+  pivot_longer(
+    cols = c(URBRUR, corruption_presidency, education, age_group),
+    names_to = "variable",
+    values_to = "category"
+  ) %>%
+  count(variable, category) %>%
+  mutate(variable = factor(variable, levels = c("URBRUR", "corruption_presidency", "education", "age_group")))
+
+# Create heatmap
+ggplot(heatmap_data, aes(x = category, y = variable, fill = n)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "lightblue", high = "darkblue") +
+  labs(
+    title = "Heatmap of Variable Distributions",
+    x = "Category",
+    y = "Variable",
+    fill = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+
+## Corruption Perceptions Vs Variables of Interest 
+```{r}
+#| label: fig-education-vs-corruption
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria  in Nigeria"
+
+cleaned_data %>%
+  count(education, corruption_presidency) %>%
+  ggplot(aes(x = corruption_presidency, y = education, fill = n)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "lightblue", high = "darkblue") +
+  labs(
+    title = "Heatmap of Education and Corruption Perceptions",
+    x = "Corruption Perception",
+    y = "Education Level",
+    fill = "Number of Respondents"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = 12, hjust = 0.5), # Reduce title size and center it
+    axis.text.x = element_text(angle = 45, hjust = 1), # Rotate x-axis labels
+    axis.text.y = element_text(size = 10) # Adjust y-axis label size
+  )
+
+```
+
+This heatmap in @fig-education-vs-corruption shows the relationship between respondents’ education levels and their perceptions of corruption in Nigeria.
+The x-axis represents corruption perception categories (All Corrupt, High Corruption, No Corruption, and Some Corruption), while the y-axis represents education levels, ranging from No Formal Schooling to Post-graduate.
+The intensity of the color reflects the number of respondents, with darker shades indicating higher counts.
+
+The heatmap reveals that respondents who completed secondary school or some secondary schooling dominate the High Corruption and Some Corruption categories.
+Respondents with higher education levels (university and post-graduate) are distributed more evenly across the corruption perception categories, with fewer concentrated in any specific category.
+Conversely, respondents with no formal schooling or only informal education are sparsely represented across all categories.
+
+This visualization highlights a notable concentration of corruption perceptions among respondents with mid-level education (secondary schooling), while those with higher education tend to have more varied perceptions.
+These findings suggest a potential link between educational attainment and experiences or attitudes toward corruption, particularly among those with secondary-level education.
+
+```{r}
+#| label: fig-age-versus-corruption
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Age Group Vs. Corruption Perception. This faceted bar chart plots the relationship between the age group of respondents and their different corruption perception levels in Nigeria."
+
+# Create the faceted bar chart
+ggplot(cleaned_data, aes(x = age_group, fill = age_group)) +
+  geom_bar() +
+  facet_wrap(~corruption_presidency) +
+  labs(
+    title = "Corruption Perceptions across Age Groups",
+    x = "Age Group",
+    y = "Count of Respondents",
+    fill = "Age Group"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set3") +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(hjust = 0.5)
+  )
+
+```
+@fig-age-versus-corruption shows the relationship between respondents' age group and their perceptions of corruption in Nigeria.
+Each panel corresponds to one of four corruption perception levels: * All Corruption, High Corruption, Some Corruption, and No Corruption.*Whitin each panel, the bars represent the count of respondent across five age groups (18-24, 25-34, 35-44, 45-54, and 55+), enabling a clear comparison of how perceptions vary by age.
+
+The 25–34 and 35–44 age groups have the highest counts in the High Corruption and Some Corruption categories, suggesting that middle-aged respondents are more likely to perceive corruption as significant.
+In contrast, younger respondents (18–24) and older respondents (55+) report lower levels of corruption perception in these categories.
+
+In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts.
+The No Corruption category has low counts across all age groups, indicating that very few respondents, regardless of age, perceive the absence of corruption.
+
+These results indicate that middle-aged respondents (25–44) are the most likely to report high levels of corruption perception, while younger and older groups report less.
+The consistently low counts in the No Corruption category reflect a widespread belief that corruption is a persistent issue in Nigeria.
+
+```{r}
+#| label: fig-ruralurban-versus-corruption
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Rural/Urban Vs.
+Corruption Perception.
+This stacked bar chart visualises the relationship between respondents' corruption perceptions and weather they live in rural or urban areas in Nigeria."
+
+# Summarize the data
+corruption_vs_urban <- cleaned_data %>%
+  count(urban_rural, corruption_presidency) %>%
+  group_by(urban_rural) %>%
+  mutate(proportion = n / sum(n)) %>%
+  ungroup()
+
+# Create the stacked bar chart
+ggplot(corruption_vs_urban, aes(x = urban_rural, y = proportion, fill = corruption_presidency)) +
+  geom_bar(stat = "identity", position = "fill") +
+  labs(
+    title = "Relationship between Rural vs. Urban Respondents and Corruption Perceptions",
+    x = "Respondent Location",
+    y = "Proportion of Respondents",
+    fill = "Corruption Perception"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1),
+    plot.title = element_text(hjust = 0.5)
+  )
+
+# Convert corruption_presidency to numeric if needed
+cleaned_data$corruption_numeric <- as.numeric(factor(cleaned_data$corruption_presidency))
+
+```
+The relationship between respondents' residential location (rural vs.
+urban) and their perceptions of corruption is shown in @fig-ruralurban-versus-corruption Each bar represents the proportion of respondents within rural and urban groups who hold different corruption perceptions: All Corrupt, High Corruption, Some Corruption, and No Corruption.
+
+The chart reveals that rural and urban respondents share similar patterns of corruption perception.
+The majority of respondents in both groups fall under the Some Corruption and High Corruption categories, with Some Corruption being slightly more prevalent.
+The All Corrupt category is the third most common perception in both groups, while the No Corruption category is consistently the least represented.
+
+These findings indicate that residential location does not significantly influence corruption perceptions, as rural and urban respondents report similar distribution patterns across all categories.
+The results suggest that perceptions of corruption are pervasive and relatively consistent across geographic locations.
+
+```{r}
+#| label: fig-gender-versus-corruption
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "Gender Vs corruption perceptions. This faceted bar chart shows the relationship between a respondents' gender and how they perceive corruption within the presidency in Nigeria."
+
+# Summarize the data
+corruption_vs_gender <- cleaned_data %>%
+  count(gender, corruption_presidency) %>%
+  group_by(gender) %>%
+  mutate(proportion = n / sum(n)) %>%
+  ungroup()
+
+# Create the faceted bar chart
+ggplot(cleaned_data, aes(x = corruption_presidency, fill = corruption_presidency)) +
+  geom_bar() +
+  facet_wrap(~gender) +
+  labs(
+    title = "Corruption Perceptions by Gender",
+    x = "Corruption Perception",
+    y = "Count of Respondents",
+    fill = "Corruption Perception"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set2") +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+@fig-gender-versus-corruption shows the the relationship between respondents' gender (male and female) and their perceptions of corruption.
+Each panel represents one gender, displaying the count of respondents across four corruption perception categories: All Corrupt, High Corruption, Some Corruption, and No Corruption.
+
+The chart shows that both male and female respondents share similar patterns of corruption perception.
+The High Corruption and Some Corruption categories have the highest counts for both genders, indicating these are the most commonly held views.
+The All Corrupt category has fewer respondents, while the No Corruption category consistently has the lowest counts for both genders.
+
+These results suggest that gender does not significantly influence perceptions of corruption, as male and female respondents exhibit similar distribution patterns across all perception categories.
+The findings highlight a shared acknowledgment of corruption as a major issue across genders in Nigeria.
+
 # Model {#sec-model}
@@
 
-## First discussion point {#sec-first-point}
+This paper looks into public perceptions of corruption within the Nigerian Presidency, using data from Afrobarometer Round 9 survey.
+A bayesian ordinal logistic regression model was used to evaluate the influence of demographic variables like education, gender, urban/rural residence, and age group on corruption perceptions.
+We found that higher education levels, urban residency, and gender play significant roles in shaping perceptions, with educated and urban individuals more likely to perceive high levels of corruption in Nigeria.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The
-discussion is a chance to show off what you know and what you learnt
-from all this.
+## The Role of Education in Shaping Corruption Perceptions {#sec-first-point}
 
-## Second discussion point
+## Urban-Rural Disparities in Perception
 
-Please don't use these as sub-heading labels - change them to be what
-your point actually is.
+## Gender Dynamics in Corruption Perception
 
-## Third discussion point
+## Policy Implications
 

### 2024-12-02 scripts/04-test_analysis_data.R

@@ -9,10 +9,6 @@
 
 
 #### Workspace setup ####
-if (!requireNamespace("testthat", quietly = TRUE)) install.packages("testthat")
-if (!requireNamespace("validate", quietly = TRUE)) install.packages("validate")
-if (!requireNamespace("pointblank", quietly = TRUE)) install.packages("pointblank")
-
 library(testthat)
 library(validate)
 library(pointblank)

### 2024-12-03 paper/paper.qmd
abstract and literature added

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "Peceptions of corruption in the Nigerian presidency vary significantly across demogrpahic groups.
+Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions.
+The results show that urban residents and yourger individuals are more likely to perceive high corruption, while rura populations and those with higher education show views that are moderate.
+These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance accountability in Nigeria"
 format: pdf
@@
 #install.packages("arrow")
-#install.packages(tinytable)
+#install.packages("tinytable")
 library(modelsummary)
@@
 
-Overview paragraph
-
-Estimand paragraph
-
-Results paragraph
-
-Why it matters paragraph
-
-Telegraphing paragraph: The remainder of this paper is structured as
-follows. @sec-data....
+Corruption is a very big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth.
+As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024].
+This paper looks into the role of demographic factors-education,gender,age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.
+
+Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways thiis can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context.
+This paper addresses this gap by making these demographics the focus.
+It does this by using nationally representative data from Afrobarometer [@afrobarometer2023], a leading survey initiative capturing public attitudes on governance, democracy, and corruption across Africa.
+A Bayesian ordinal logistic regression was used to find patterns in how education, gender, age, and geographic location influence perceptions of corruption.
+
+Our paper shows that there are alot of disparities in corruption perceptions across demographic groups.
+Younger respondents and urban residents have higher perceptions of corruption, likely because of higer exposure to investigative media and political discourse.
+In contrast, rural populations-often reliant on patronage systems- tend to report more neutral views.
+Education also plays an important role since we find that secondary school graduates have the highest corruption perceptions.
+
+Understanding these demographic differences is important for designing effective anti-corruption campaigns.
+Making sure outreach efforts are tailored to the unique experiences and perceptions of different demographic groups can increase their effectiveness and increase public trust.
+For example, youth-focused campaigns that leverage social media platforms and urban outreach using investigative journalism can engage the people.
+At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations.
+A the UNODC emphasizes, 'targeted and effective anti-corruption policies will improve likes of Nigerian citizens" [@afrobarometer2023].
+
+The remainder of this paper is structured as follows; @sec-data detailed the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest.
+@sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria.
+@sec-discussion examines these results, discussing their implications for anti-corruption policies, weaknesses and next steps.
+@sec-survey-appendix explores the details of the Afrobarometer survey.
+@sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.
 
@@
 topics like governance, democracy, and economic issues. The Nigerian
-Round 9 survey dataset contains responses from 1,556 people and shows the diverse demographic statistics across gender, region,
-and residence type(urban or rural). The data is freely available on the
-Afrobarometer website[@afrobarometer2023] and was collected through a
-multi-stage, stratified sampling method. This is to ensure
-representativeness and enables analysis of different demographics and
-socioeconomic indicators.
+Round 9 survey dataset contains responses from 1,556 people and shows
+the diverse demographic statistics across gender, region, and residence
+type(urban or rural). The data is freely available on the Afrobarometer
+website[@afrobarometer2023] and was collected through a multi-stage,
+stratified sampling method. This is to ensure representativeness and
+enables analysis of different demographics and socioeconomic indicators.
 
@@
 
-The data for this study was downloaded, cleaned, analyzed, modeled, and visualized using R [@citeR], a statistical programming language. The following packages were used:
-
-- **`modelsummary`** [@modelsummary]: Used to create well-formatted regression tables and summaries.
-- **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling using the Stan backend.
-- **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation, and summarization processes.
-- **`here`** [@here]: Simplified the organization of file paths, improving project reproducibility.
-- **`arrow`** [@arrow]: Enabled efficient handling of large datasets with fast reading and writing capabilities.
-- **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic checks and posterior predictive visualizations for Bayesian models.
-- **`ggplot2`** [@ggplot2]: Provided extensive tools for creating clear and impactful visualizations.
-- **`patchwork`** [@patchwork]: Combined multiple plots into cohesive, professional visuals.
-- **`knitr`** [@knitr]: Enabled dynamic report generation, integrating code, output, and text seamlessly.
-- **`kableExtra`** [@kableExtra]: Enhanced table styling and formatting for clean, professional presentations.
-- **`ggalt`** [@ggalt]: Allowed the creation of specialized plots, enhancing the depth of data visualizations.
-- **`haven`** [@haven]: Facilitated the import of `.sav` survey data from the Afrobarometer.
-- **`broom.mixed`** [@broommixed]: Streamlined the extraction and tidying of results from mixed models for easy analysis and visualization.
-- **`afrobarometer`** [@afrobarometer2023]: Served as the primary data source, providing valuable survey data for analysis.
-- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies.
+The data for this study was downloaded, cleaned, analyzed, modeled, and
+visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing valuable survey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies.
+The
+following packages were used:
+
+-   **`modelsummary`** [@modelsummary]: Used to create well-formatted
+    regression tables and summaries.
+-   **`rstanarm`** [@rstanarm]: Facilitated Bayesian regression modeling
+    using the Stan backend.
+-   **`dplyr`** [@dplyr]: Streamlined data manipulation, transformation,
+    and summarization processes.
+-   **`here`** [@here]: Simplified the organization of file paths,
+    improving project reproducibility.
+-   **`arrow`** [@arrow]: Enabled efficient handling of large datasets
+    with fast reading and writing capabilities.
+-   **`bayesplot`** [@bayesplot]: Assisted in producing diagnostic
+    checks and posterior predictive visualizations for Bayesian models.
+-   **`ggplot2`** [@ggplot2]: Provided extensive tools for creating
+    clear and impactful visualizations.
+-   **`patchwork`** [@patchwork]: Combined multiple plots into cohesive,
+    professional visuals.
+-   **`knitr`** [@knitr]: Enabled dynamic report generation, integrating
+    code, output, and text seamlessly.
+-   **`kableExtra`** [@kableExtra]: Enhanced table styling and
+    formatting for clean, professional presentations.
+-   **`ggalt`** [@ggalt]: Allowed the creation of specialized plots,
+    enhancing the depth of data visualizations.
+-   **`haven`** [@haven]: Facilitated the import of `.sav` survey data
+    from the Afrobarometer.
+-   **`broom.mixed`** [@broommixed]: Streamlined the extraction and
+    tidying of results from mixed models for easy analysis and
+    visualization.
+-   ***Telling Stories with Data*** [@tellingstories]: This book was
+    referenced for its code and methodologies.
 
 ## Cleaned Data Overview
+
 ```{r}
@@
 ```
-The cleaned dataset used in this study is summarised in @tbl-summary-statistics, which provides key statistics to offer an overview of the dataset's structure and characteristics.
-The most frequent age group among respondents is identified, representing the predominant demographic in terms of age.
-The table also highlights the urban and male percentages, which indicate the proportion of urban residents (43.38%) and male respondents (49.68%) in the sample.
-
-Further, the table breaks down the perceptions of corruption into four categories—"None," "Some," "High," and "All"—with counts for each, offering insights into respondents' views on corruption in the presidency.
-Additionally, the table details the distribution of respondents across education levels, including categories such as "Primary," "Secondary," "University," and "Postgraduate." Together, these summary statistics provide a comprehensive snapshot of the dataset, enabling a clear understanding of its demographic and categorical variables.
-
-## Variables of Interest
-```{r}
-#| label: fig-urban-rural-distribution
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: " Urban vs Rural Respondent Distribution. This bar chart compares the number of respondents residing in urban versus rural areas in Nigeria."
-
-# Plot: Urban vs Rural Respondent Distribution
-cleaned_data %>%
-  count(URBRUR) %>%
-  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
-  geom_bar(stat = "identity") +
-  labs(
-    title = "Urban vs Rural Respondent Distribution",
-    x = "Respondent Location",
-    y = "Number of Respondents"
-  ) +
-  theme_minimal() +
-  scale_fill_manual(
-    values = c("Urban Residents" = "blue", "Rural Residents" = "gray")
-  ) +
-  guides(fill = "none")
-
-```
-
-@fig-urban-rural-distribution illustrates the distribution of survey
-respondents based on their residential location, categorized as urban or
-rural. From this, we see that the sample has more rural residents
-compared to urban residents. Specifically, the Afrobarometer survey for
-Nigeria, conducted in 2022, reports that approximately 53% of Nigeria's
-population resides in rural areas, this is is consistent with national
-demographic trends [@worldbank2022rural]. This rural-urban distribution
-is important for helping us understand the perspectives seen in the
-survey, since rural populations may have different challenges in
-governance and corruption compared to urban populations. The imbalance
-in representation shows that looking at geographical disparities when
-interpreting results from nationwide surveys is important.
-
-```{r}
-#| label: fig-corruption-presidency
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "Perceived Corruption in the Presidency. This bar chart shows the distribution of respondents' perceptions of corruption in the presidency in Nigeria."
-
-# Plot: Perceived Corruption in the Presidency
-cleaned_data %>%
-  count(corruption_presidency) %>%
-  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
-  geom_bar(stat = "identity") +
-  labs(
-    title = "Perceived Corruption in the Presidency",
-    x = "Perception of Corruption",
-    y = "Number of Respondents"
-  ) +
-  theme_minimal() +
-  scale_fill_manual(
-    values = c("No Corruption" = "green", 
-               "Some Corruption" = "yellow", 
-               "High Corruption" = "red", 
-               "All Corrupt" = "purple")
-  ) +
-  guides(fill = "none")
-
-```
-
- @fig-corruption-presidency presents the distribution of respondents'
-perceptions of corruption within the Nigerian presidency. The variable
-"Perceived Corruption in the Presidency" captures respondents'
-perceptions of the extent of corruption within the Nigerian presidency
-and its officials. This variable originates from Question 38A of the
-Afrobarometer survey, which asked: *"How many of the following people do
-you think are involved in corruption, or haven’t you heard enough about
-them to say: the president and officials in his office?"*
-[@Afrobarometer2022codebook] Respondents could choose from the following
-values:
-
--   **0 (None)**: Indicates that the respondent perceives no corruption
-    in the office of the presidency.
--   **1 (Some of them)**: Suggests that the respondent believes a few
-    individuals in the presidency are involved in corruption.
--   **2 (Most of them)**: Reflects the perception that corruption is
-    prevalent among the majority of the presidency's officials.
--   **3 (All of them)**: Suggests the respondent perceives widespread
-    corruption, implicating all officials in the presidency.
--   **8 (Refused)**: Indicates the respondent declined to answer the
-    question.
--   **9 (Don’t know/Haven’t heard enough)**: Suggests the respondent was
-    unsure or lacked sufficient knowledge to provide an answer.
--   **-1 (Missing)**: Represents missing or unavailable responses.
-
-For the analysis, only the substantive responses (0-3) were considered,
-in order to help us look into perceptions of corruption within the
-presidency. The high frequency of responses in the "High Corruption" and
-"Some Corruption" categories reflects persistent concerns about the
-integrity of key officials in Nigeria, aligning with broader findings on
-corruption in the region. @fig-corruption-presidency presents the
-distribution of respondents' perceptions of corruption within the
-Nigerian presidency. Among these, the category "High corruption" is the
-most frequently reported, followed by "Some corruption". "All corrupt"
-ranks third, with "No Corruption" being the least chosen category which
-is no surprise given our data is in the context of Nigeria. These
-proportions show significant public concern about corruption within the
-presidency, consistent with broader trends in public concern abut
-corruption corruption within the presidency in Nigeria.
-
-```{r}
-#| label: fig-dumbbell-education
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "Distribution of Education Levels in Nigeria"
-#install.packages("ggalt")
-library(ggalt)
-
-cleaned_data %>%
-  count(education) %>%
-  ggplot(aes(x = n, y = reorder(education, n))) +
-  geom_dumbbell(
-    aes(xend = 0, x = n), 
-    size = 3, colour = "darkblue", dot_guide = TRUE
-  ) +
-  theme_minimal() +
-  labs(
-    title = "Distribution of Education Levels in Nigeria",
-    x = "Number of Respondents", y = "Education Level"
-  )
-
-```
-
-@fig-dumbbell-education visually represents the educational attainment
-levels of respondents in the Afrobarometer survey for Nigeria. The data
-reflects responses to the question: *What is your highest level of
-education?*. The chart indicates that the most frequent reported level
-of education is "secondary school completed," followed by "primary
-school completed" and "no formal schooling". Fewer respondents reported
-having attained "post secondary qualifications," "university completed,"
-or "Post-graduate" education, shows the disparity in advanced
-educational attainment across the population. This distribution shows
-that basic education levels are more prevalent among respondents, which
-may influence their perceptions and responses in the broader survey.
-Including educational attainment is important in our analysis because it
-is an important socioeconomic factor.
-
-```{r}
-#| label: fig-age-group-distribution
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "Age Group Distribution. This bar chart displays the number of respondents in each age group in Nigeria."
-
-# Plot: Age Group Distribution
-cleaned_data %>%
-  count(age_group) %>%
-  ggplot(aes(x = age_group, y = n, fill = age_group)) +
-  geom_bar(stat = "identity") +
-  labs(
-    title = "Age Group Distribution",
-    x = "Age Group",
-    y = "Number of Respondents"
-  ) +
-  theme_minimal() +
-  scale_fill_brewer(palette = "Set3") +
-  guides(fill = "none")
-
-```
-
-@fig-age-group-distribution illustrates the distribution of survey
-respondents across five distinct age groups: 18-24, 25-34, 35-44, 45-54,
-and 55+. The data reveals that the 25-34 age group is the most
-represented, with over 500 respondents, followed by the 35-44 age group.
-The youngest cohort, aged 18-24, comprises approximately 300
-respondents, while the older age groups (45-54 and 55+) are less
-represented in the dataset, with fewer than 200 respondents each. This
-distribution highlights a concentration of responses from younger
-demographics, particularly those aged 25-34, which may reflect broader
-societal trends such as population age structure or survey reach and
-accessibility.
-
-## Combined variables of interest?
-
-```{r}
-#| label: fig-variables-of-interest
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "combined variables of interest"
-
-library(patchwork)
-
-# Create individual plots
-urban_plot <- cleaned_data %>%
-  count(URBRUR) %>%
-  ggplot(aes(x = URBRUR, y = n, fill = URBRUR)) +
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  labs(title = "Urban vs Rural", x = "Location", y = "Count")
-
-corruption_plot <- cleaned_data %>%
-  count(corruption_presidency) %>%
-  ggplot(aes(x = corruption_presidency, y = n, fill = corruption_presidency)) +
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  labs(title = "Corruption Perception", x = "Perception", y = "Count")
-
-education_plot <- cleaned_data %>%
-  count(education) %>%
-  ggplot(aes(x = n, y = reorder(education, n))) +
-  geom_col(fill = "darkblue") +
-  theme_minimal() +
-  labs(title = "Education Level", x = "Count", y = "Education")
-
-age_plot <- cleaned_data %>%
-  count(age_group) %>%
-  ggplot(aes(x = age_group, y = n, fill = age_group)) +
-  geom_bar(stat = "identity") +
-  theme_minimal() +
-  labs(title = "Age Distribution", x = "Age Group", y = "Count")
-
-# Combine plots
-urban_plot + corruption_plot + education_plot + age_plot +
-  plot_layout(ncol = 2)
-
-```
-
-```{r}
-#| label: fig-variables-of-interest-heatmap
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "combined variables of interest"
-
-#install.packages("tidyr")
-library(tidyr)
-# Combine data for heatmap
-heatmap_data <- cleaned_data %>%
-  pivot_longer(
-    cols = c(URBRUR, corruption_presidency, education, age_group),
-    names_to = "variable",
-    values_to = "category"
-  ) %>%
-  count(variable, category) %>%
-  mutate(variable = factor(variable, levels = c("URBRUR", "corruption_presidency", "education", "age_group")))
-
-# Create heatmap
-ggplot(heatmap_data, aes(x = category, y = variable, fill = n)) +
-  geom_tile(color = "white") +
-  scale_fill_gradient(low = "lightblue", high = "darkblue") +
-  labs(
-    title = "Heatmap of Variable Distributions",
-    x = "Category",
-    y = "Variable",
-    fill = "Count"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-
-```
+
+The cleaned dataset used in this study is summarised in
+@tbl-summary-statistics, which provides key statistics to offer an
+overview of the dataset's structure and characteristics. The most
+frequent age group among respondents is identified, representing the
+predominant demographic in terms of age. The table also highlights the
+urban and male percentages, which indicate the proportion of urban
+residents (43.38%) and male respondents (49.68%) in the sample.
+
+Further, the table breaks down the perceptions of corruption into four
+categories—"None," "Some," "High," and "All"—with counts for each,
+offering insights into respondents' views on corruption in the
+presidency. Additionally, the table details the distribution of
+respondents across education levels, including categories such as
+"Primary," "Secondary," "University," and "Postgraduate." Together,
+these summary statistics provide a comprehensive snapshot of the
+dataset, enabling a clear understanding of its demographic and
+categorical variables.
 
 ## Corruption Perceptions Vs Variables of Interest
+
 ```{r}
@@
 
-This heatmap in @fig-education-vs-corruption shows the relationship between respondents’ education levels and their perceptions of corruption in Nigeria.
-The x-axis represents corruption perception categories (All Corrupt, High Corruption, No Corruption, and Some Corruption), while the y-axis represents education levels, ranging from No Formal Schooling to Post-graduate.
-The intensity of the color reflects the number of respondents, with darker shades indicating higher counts.
-
-The heatmap reveals that respondents who completed secondary school or some secondary schooling dominate the High Corruption and Some Corruption categories.
-Respondents with higher education levels (university and post-graduate) are distributed more evenly across the corruption perception categories, with fewer concentrated in any specific category.
-Conversely, respondents with no formal schooling or only informal education are sparsely represented across all categories.
-
-This visualization highlights a notable concentration of corruption perceptions among respondents with mid-level education (secondary schooling), while those with higher education tend to have more varied perceptions.
-These findings suggest a potential link between educational attainment and experiences or attitudes toward corruption, particularly among those with secondary-level education.
+This heatmap in @fig-education-vs-corruption shows the relationship
+between respondents’ education levels and their perceptions of
+corruption in Nigeria. The data reflects responses to the question:
+*What is your highest level of education?*.The x-axis represents
+corruption perception categories (All Corrupt, High Corruption, No
+Corruption, and Some Corruption), while the y-axis represents education
+levels, ranging from No Formal Schooling to Post-graduate. The intensity
+of the color reflects the number of respondents, with darker shades
+indicating higher counts.
+
+The heatmap reveals that respondents who completed secondary school or
+some secondary schooling dominate the High Corruption and Some
+Corruption categories. Respondents with higher education levels
+(university and post-graduate) are distributed more evenly across the
+corruption perception categories, with fewer concentrated in any
+specific category. Conversely, respondents with no formal schooling or
+only informal education are sparsely represented across all
+categories.There is a notable concentration of corruption perceptions
+among respondents with mid-level education (secondary schooling), while
+those with higher education tend to have more varied perceptions. These
+findings suggest a potential link between educational attainment and
+experiences or attitudes toward corruption, particularly among those
+with secondary-level education.
 
@@
 ```
-@fig-age-versus-corruption shows the relationship between respondents' age group and their perceptions of corruption in Nigeria.
-Each panel corresponds to one of four corruption perception levels: * All Corruption, High Corruption, Some Corruption, and No Corruption.*Whitin each panel, the bars represent the count of respondent across five age groups (18-24, 25-34, 35-44, 45-54, and 55+), enabling a clear comparison of how perceptions vary by age.
-
-The 25–34 and 35–44 age groups have the highest counts in the High Corruption and Some Corruption categories, suggesting that middle-aged respondents are more likely to perceive corruption as significant.
-In contrast, younger respondents (18–24) and older respondents (55+) report lower levels of corruption perception in these categories.
-
-In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts.
-The No Corruption category has low counts across all age groups, indicating that very few respondents, regardless of age, perceive the absence of corruption.
-
-These results indicate that middle-aged respondents (25–44) are the most likely to report high levels of corruption perception, while younger and older groups report less.
-The consistently low counts in the No Corruption category reflect a widespread belief that corruption is a persistent issue in Nigeria.
+
+@fig-age-versus-corruption shows the relationship between respondents'
+age group which was obtained by asking the respondent *How old are you?* and their perceptions of corruption in Nigeria. Each panel corresponds to one of four corruption perception levels. Within
+each panel, the bars represent the count of respondent across five age
+groups (18-24, 25-34, 35-44, 45-54, and 55+), enabling a clear
+comparison of how perceptions vary by age.
+
+The 25–34 and 35–44 age groups have the highest counts in the High
+Corruption and Some Corruption categories, suggesting that middle-aged
+respondents are more likely to perceive corruption as significant. In
+contrast, younger respondents (18–24) and older respondents (55+) report
+lower levels of corruption perception in these categories.In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts. The No
+Corruption category has low counts across all age groups, indicating
+that very few respondents, regardless of age, perceive the absence of
+corruption.
+
+These results indicate that middle-aged respondents (25–44) are the most
+likely to report high levels of corruption perception, while younger and
+older groups report less. The consistently low counts in the No
+Corruption category reflect a widespread belief that corruption is a
+persistent issue in Nigeria.
 
@@
 
-# Convert corruption_presidency to numeric if needed
+# Convert corruption_presidency to numeric 
 cleaned_data$corruption_numeric <- as.numeric(factor(cleaned_data$corruption_presidency))
@@
 ```
+
 The relationship between respondents' residential location (rural vs.
-urban) and their perceptions of corruption is shown in @fig-ruralurban-versus-corruption Each bar represents the proportion of respondents within rural and urban groups who hold different corruption perceptions: All Corrupt, High Corruption, Some Corruption, and No Corruption.
-
-The chart reveals that rural and urban respondents share similar patterns of corruption perception.
-The majority of respondents in both groups fall under the Some Corruption and High Corruption categories, with Some Corruption being slightly more prevalent.
-The All Corrupt category is the third most common perception in both groups, while the No Corruption category is consistently the least represented.
-
-These findings indicate that residential location does not significantly influence corruption perceptions, as rural and urban respondents report similar distribution patterns across all categories.
-The results suggest that perceptions of corruption are pervasive and relatively consistent across geographic locations.
+urban) and their perceptions of corruption is shown in
+@fig-ruralurban-versus-corruption Each bar represents the proportion of
+respondents within rural and urban groups who hold different corruption
+perceptions.
+
+The chart reveals that rural and urban respondents share similar
+patterns of corruption perception. The majority of respondents in both
+groups fall under the Some Corruption and High Corruption categories,
+with Some Corruption being slightly more prevalent. The All Corrupt
+category is the third most common perception in both groups, while the
+No Corruption category is consistently the least represented.
+
+Residential location does not significantly influence corruption perceptions, as
+rural and urban respondents report similar distribution patterns across all 
+categories. The results suggest that perceptions of corruption are pervasive and
+relatively consistent across geographic locations.
 
@@
 ```
-@fig-gender-versus-corruption shows the the relationship between respondents' gender (male and female) and their perceptions of corruption.
-Each panel represents one gender, displaying the count of respondents across four corruption perception categories: All Corrupt, High Corruption, Some Corruption, and No Corruption.
-
-The chart shows that both male and female respondents share similar patterns of corruption perception.
-The High Corruption and Some Corruption categories have the highest counts for both genders, indicating these are the most commonly held views.
-The All Corrupt category has fewer respondents, while the No Corruption category consistently has the lowest counts for both genders.
-
-These results suggest that gender does not significantly influence perceptions of corruption, as male and female respondents exhibit similar distribution patterns across all perception categories.
-The findings highlight a shared acknowledgment of corruption as a major issue across genders in Nigeria.
+
+@fig-gender-versus-corruption shows the the relationship between
+respondents' gender (male and female) and their perceptions of
+corruption. Each panel represents one gender, displaying the count of
+respondents across four corruption perception categories: All Corrupt,
+High Corruption, Some Corruption, and No Corruption.
+
+The chart shows that both male and female respondents share similar
+patterns of corruption perception. The High Corruption and Some
+Corruption categories have the highest counts for both genders,
+indicating these are the most commonly held views. The All Corrupt
+category has fewer respondents, while the No Corruption category
+consistently has the lowest counts for both genders.
 
@@
 
-# Results
+# Results {#sec-results}
 
@@
 The analysis revealed distinct trends in Corruption perceptions in
-different demographics. Our results are summarized in @tbl-modelresults.This presents the estimated coefficients and standard
+different demographics. Our results are summarized in @tbl-modelresults. 
+This presents the estimated coefficients and standard
 errors for each predictor included in the model. The dependent variable
@@
 
-# Discussion
-
-This paper looks into public perceptions of corruption within the Nigerian Presidency, using data from Afrobarometer Round 9 survey.
-A bayesian ordinal logistic regression model was used to evaluate the influence of demographic variables like education, gender, urban/rural residence, and age group on corruption perceptions.
-We found that higher education levels, urban residency, and gender play significant roles in shaping perceptions, with educated and urban individuals more likely to perceive high levels of corruption in Nigeria.
-
-## The Role of Education in Shaping Corruption Perceptions {#sec-first-point}
-
-## Urban-Rural Disparities in Perception
-
-## Gender Dynamics in Corruption Perception
+# Discussion {#sec-discussion}
+
+This paper looks into the demographic disparities of corruption
+perception in the Nigerian presidency, using survey data to examine
+variables like education, gender, age and urban versus rural residence.
+By looking at these factors, the study aims to inform targeted
+anti-corruption camapigns and policy making. The Bayesian modeling
+approach helps us understand the relationship between corruption
+perceptions and these demographic variables.
+
+## Tareting Education Levels in Anti-Corruption Campaigns {#sec-first-point}
+
+The relationship between education and corruption perceptions shows that
+respondents with secondary school education are the most likely to
+perceive high levels of corruption in the presidency. This supports
+broader research showing that moderate levels of education are linked to
+increased political awareness and accountability demands, as individuals
+in this group are better equipped to identify systemic corruption but
+may lack the structural access to address it effectively
+[@transparency2019]. Individuals with higher education, such as
+university graduates, report more moderate corruption perceptions, this
+might largely beceause of their exposure to diverse viewpoints and
+greater access to institutional frameworks that allow for political
+skepticism. These suggest that anti-corruption campaigns targeting this
+moderately educated demographic should focus on actionable reforms and
+accountability mechanisms to harness their heightened awareness
+productively [@u4nigeria2023].
+
+## Urban-Rural Dynamics in Perception
+
+Urban respondents are somewhat more likely than their rural counterparts
+to perceive high corruption in the presidency. This is consistent with
+findings that urban populations have greater access to investigative
+reporting and public discourse on corruption, which can amplify
+awareness and perceptions [@u4nigeria2023]. On the other hand, rural
+respondents, who may rely on localized patronage networks for essential
+services, often exhibit more neutral or unclear perceptions of
+corruption, influenced by limited media access and dependency on these
+informal systems. Campaigns should focus on leveraging urban platforms
+like social media, community-based programs, and public dialogues to
+engage critical urban audiences, while also expanding rural outreach
+through local radio, grassroots organizations, and educational
+interventions tailored to these settings.
+
+## The Role of Age, Youth & Gender Engagement
+
+Younger respondents, particularly those aged 25–34, consistently report
+higher perceptions of corruption compared to older age groups. This
+aligns with existing research that highlights younger demographics as
+more vocal in their demands for systemic change in a country like
+Nigeria, where over 60% of the population is under 25 [@UNFPA2023],
+targeted anti-corruption initiatives that harness youth energy are
+important. These efforts should include digital campaigns on platforms
+frequently used by younger audiences, interactive town hall discussions,
+and youth-led advocacy initiatives that focus on transparency and
+accountability. Importantly, such campaigns need to have clear pathways
+for action, making it easy for youth to channel their frustration into
+productive engagement with governance structures.
+
+While gender differences in corruption perceptions were less pronounced
+in our paper, prior research shows that women often experience
+corruption indirectly, particularly in accessing healthcare or education
+systems [@GenderCorruption2021]. This shows the need for anti-corruption
+campaigns that address systemic barriers disproportionately impacting
+women, emphasizing institutional reforms in sectors that are important
+to gender equity. Moreover, trust in institutions plays an important
+role in shaping perceptions. Corruption scandals and perceived impunity
+have a way of eroding trust, particularly in urban areas where political
+engagement is higher[@afrobarometer2007]. Restoring institutional
+credibility through transparency and consistent enforcement of
+anti-corruption measures can increase the effectiveness of campaigns
+targeting both genders.
 
@@
 
+This paper is focused on looking at trends in the corruption perception
+between different demographics and seeing how these differences can be
+leveraged to maximize anti corruption campaigns and policy in
+Nigeria.From this paper, we find different actionable strategies for
+improving the effectiveness of anti-corruption campaigns in Nigeria.
+First, targeting rural and urban populations differently might be
+effective. Urban residents, who have greater access to investigative
+media and public debates, are more likely to perceive high corruption.
+Campaigns in urban areas should therefore focus on digital platforms
+like social media and mobile apps, as well as partnerships with
+investigative journalists and public accountability platforms to engage
+this group effectively. In rural areas, where reliance on patronage
+systems and limited media access shape perceptions, grassroots
+communication strategies like community radio, local town halls, and
+collaborations with trusted community leaders are better suited to
+disseminate anti-corruption messaging.
+
+Education also emerges as a key determinant of corruption perceptions.
+Secondary school graduates exhibit the highest levels of awareness, this
+suggests that civic education campaigns should focus on this demographic
+to harness their increased engagement. Integrating anti-corruption
+education into school curricula could early awareness and long-term
+attitudinal changes.Youth engagement is very important, given that
+younger age groups, particularly those aged 25–34, report the highest
+levels of dissatisfaction with corruption. Social media campaigns
+tailored to platforms popular with youth, together with interactive town
+hall discussions and youth-led grassroots initiatives, could channel
+this demographic's energy into organized anti-corruption efforts.
+
+Lastly, rebuilding public trust in institutions should be a priority.
+Transparent hiring practices, visible enforcement of anti-corruption
+laws, and strengthened whistleblower protections are important steps to
+showing institutional accountability. Localized outreach through
+community leaders can also help bridge the trust gap, particularly in
+rural settings. Policymakers should put these findings into a
+data-driven framework so they can adapt strategies based on demographic
+trends and feedback.
+
 ## Weaknesses and next steps
 
-Weaknesses and next steps should also be included.
+While this paper tells us a lot about the demographic distributions of
+corruption perception about the presidency in Nigeria, there are a few
+limitations that have to be considered. The survey data relies on
+self-reported perception, which can be influenced by social desirability
+bias which refers to the situation where respondents' endorse more
+favorable responses in order to enhance their own
+self-presentation[@bias2022].For example, high-profile corruption
+scandals or electoral promises happening close to survey periods may
+distort responses. The data does not account for regional differences
+within these urban rural classifications, which could change the
+understanding of corruption perceptions further.The last limitation is
+with the bayesian model, because while the Bayesian model accounts for
+uncertainty, it does not address potential unobserved variables, like
+political affiliations or socioeconomic status, which may affect the
+relationships we say.
+
+Future research should look more into longitudinal trends in corruption
+perceptions to look at how demographic factors evolve over time. This
+could be achieve through tracking respondents across electoral cycles or
+policy interventions to observe shifts in attitudes. Additionally,
+looking more into regional subcategories could show us some localized
+patterns, particularly in states that have different governing
+structures and resource allocation systems. Expanding the dataset to
+include qualitative information from interviews and focus groups would
+also give more information about how demographic characteristics relate
+to peoples' lived corruption experiences.
 
@@
 
+# Surveys, Sampling, and Observational Data {#sec-survey-appendix}
+
+## Survey Methodolgy and Design
+
+## Sampling Techniques
+
+## Observational Data Challenges
+
+## Proposed Improvements
+
 # Additional data details
+
+```{r}
+#| label: fig-variables-of-interest-heatmap
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+#| fig.cap: "combined variables of interest"
+
+#install.packages("tidyr")
+library(tidyr)
+# Combine data for heatmap
+heatmap_data <- cleaned_data %>%
+  pivot_longer(
+    cols = c(URBRUR, corruption_presidency, education, age_group),
+    names_to = "variable",
+    values_to = "category"
+  ) %>%
+  count(variable, category) %>%
+  mutate(variable = factor(variable, levels = c("URBRUR", "corruption_presidency", "education", "age_group")))
+
+# Create heatmap
+ggplot(heatmap_data, aes(x = category, y = variable, fill = n)) +
+  geom_tile(color = "white") +
+  scale_fill_gradient(low = "lightblue", high = "darkblue") +
+  labs(
+    title = "Heatmap of Variable Distributions",
+    x = "Category",
+    y = "Variable",
+    fill = "Count"
+  ) +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+
+![Combined plot](combined_plot.png){width="120%"}
 
@@
     y = "Density"
+  ) + 
+  scale_x_continuous(
+    name = "Observed Data",     
+    breaks = seq(0, 1, by = 0.1), 
+    limits = c(1.1, 2.8)             
   )
@@
 #| warning: false
-#| label: fig-diagnostic-ppcheck
-#| fig-cap: "Posterior Predictive Check for the Bayesian ordinal logistic regression model."
-
-# Posterior Predictive Check
-pp_check(bayesian_model) +
-  theme_classic() +
-  labs(
-    title = "Posterior Predictive Check",
-    x = "Observed Data",
-    y = "Density"
-  )
-
-```
-
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
 #| label: fig-diagnostic-traceplot

### 2024-12-03 other/datasheet/datasheet.qmd
datasheet & ethics

---
title: "Datasheet for 'Afrobarometer Round 9 Nigeria Survey'"
author: 
  - Fatimah Yunusa
thanks: "all information used to compile this datasheet was obtained from the following: [Afrobarometer Survey Manual](https://www.afrobarometer.org/wp-content/uploads/2022/07/AB_R9.-Survey-Manual_eng_FINAL_20jul22.pdf), [Nigeria Round 9 codebook 2022](https://www.afrobarometer.org/survey-resource/nigeria-round-9-codebook-2022/) "
date: today
date-format: long
abstract: "This datasheet describes the Afrobarometer Round 9 Nigeria survey dataset, which explores public perceptions of governance, corruption, and socio-political dynamics in Nigeria. The dataset comprises responses from Nigerian citizens aged 18 and older, collected using a robust sampling methodology designed to ensure representativeness. The survey data inform research on demographic and geographic factors influencing public opinion, with applications in governance, policy-making, and academic research."
format: pdf
toc: true
number-sections: true
---

## **Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to provide insights into public attitudes on governance, corruption, democracy, and socio-economic issues in Africa, particularly Nigeria. It addresses the need for representative, standardized data on public opinion to inform policy-making, academic research, and civic engagement.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was created by Afrobarometer, a pan-African research organization, in partnership with local country teams in Nigeria.

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Afrobarometer is funded by multiple international organizations, including the Swedish International Development Cooperation Agency (SIDA), USAID, and the Mo Ibrahim Foundation.

4. *Any other comments?*
    - This dataset is part of a larger effort to collect comparable public opinion data across Africa.

## **Composition**

1. *What do the instances that comprise the dataset represent?*
	- The dataset represents individual survey responses from Nigerian citizens aged 18 and older.

2. *How many instances are there in total?*
	- The dataset includes approximately 2,400 individual responses.

3. *Does the dataset contain all possible instances or is it a sample from a larger set?*
	- The dataset is a probability sample representing the adult population of Nigeria. It is stratified by gender, urban/rural location, and geographic region to ensure representativeness.

4. *What data does each instance consist of?*
	- Each instance includes raw survey responses, such as demographic information (e.g., age, gender, education), and responses to opinion questions on governance, corruption, and democracy.

5. *Is there a label or target associated with each instance?*
	- The primary variable of interest is "perception of corruption in the presidency," measured on an ordinal scale.

6. *Is any information missing from individual instances?*
	- Some responses are missing due to non-responses or participants declining to answer specific questions.

7. *Are relationships between individual instances made explicit?*
	- No, each survey response is independent.

8. *Are there recommended data splits?*
	- No recommended splits are provided as the dataset is observational and intended for analysis.

9. *Are there any errors, sources of noise, or redundancies in the dataset?*
	- Potential sources of noise include respondent misinterpretation of questions and social desirability bias.

10. *Is the dataset self-contained, or does it link to external resources?*
	- The dataset is self-contained, with supplementary documentation available on Afrobarometer's website.

11. *Does the dataset contain data that might be considered confidential?*
	- No personal identifiers are included, ensuring anonymity.

12. *Does the dataset contain potentially offensive data?*
	- No, but responses on corruption perceptions may evoke strong opinions.

13. *Does the dataset identify any sub-populations?*
	- Yes, demographic sub-populations such as age, gender, and geographic region are identified.

14. *Is it possible to identify individuals from the dataset?*
	- No, all responses are anonymized.

15. *Does the dataset contain data that might be considered sensitive?*
	- Yes, responses on corruption perceptions may reflect sensitive political opinions.

16. *Any other comments?*
	- The dataset provides a unique opportunity to analyze public attitudes toward governance in Nigeria.

## **Collection Process**

1. *How was the data acquired?*
	- Data were collected through face-to-face interviews using a standardized questionnaire.

2. *What mechanisms or procedures were used to collect the data?*
	- Trained enumerators conducted in-person interviews following Afrobarometer's standardized methodology.

3. *What was the sampling strategy?*
	- A stratified, clustered, multi-stage, probability sampling design was used, with random selection at each stage.

4. *Who was involved in the data collection process and how were they compensated?*
	- Local enumerators were hired and compensated based on Afrobarometer's guidelines.

5. *Over what timeframe was the data collected?*
	- Data collection for Round 9 in Nigeria occurred over a period of several weeks in 2022.

6. *Were any ethical review processes conducted?*
	- Ethical reviews were conducted by Afrobarometer-affiliated institutions, including the University of Cape Town's ethics board.

7. *Did you collect the data directly or obtain it via third parties?*
	- Afrobarometer collected the data directly through trained field teams.

8. *Were individuals notified about the data collection?*
	- Yes, individuals were informed during the consent process.

9. *Did individuals consent to the collection and use of their data?*
	- Verbal consent was obtained from all participants.

10. *Was there a mechanism to revoke consent?*
	- Participants could decline to answer questions or terminate the interview at any time.

11. *Has an analysis of the potential impact of the dataset been conducted?*
	- Yes, Afrobarometer considers the social and political sensitivities of its data collection processes.

12. *Any other comments?*
	- Afrobarometer’s methods prioritize participant dignity and safety.

## **Preprocessing/Cleaning/Labeling**

1. *Was any preprocessing/cleaning/labeling of the data done?*
	- Yes, data were cleaned to remove incomplete or invalid responses.

2. *Was the "raw" data saved in addition to the preprocessed data?*
	- Yes, raw data are stored securely for archival purposes.

3. *Is the preprocessing software available?*
	- Afrobarometer’s data processing scripts are not publicly available.

4. *Any other comments?*
	- Preprocessing ensures data integrity and consistency.

## **Uses**

1. *Has the dataset been used for any tasks already?*
	- Yes, it has been used for research on governance, democracy, and public opinion.

2. *Is there a repository that links to all papers using the dataset?*
	- Afrobarometer maintains a database of publications using its datasets.

3. *What (other) tasks could the dataset be used for?*
	- The dataset could inform policy-making, academic studies, and civic advocacy.

4. *Are there tasks for which the dataset should not be used?*
	- The dataset should not be used to misrepresent public opinion or marginalize specific groups.

## **Distribution**

1. *Will the dataset be distributed to third parties?*
	- Yes, it is publicly available on Afrobarometer’s website.

2. *How will the dataset be distributed?*
	- Through Afrobarometer’s online data portal, free of charge.

3. *When will the dataset be distributed?*
	- It is already publicly available.

4. *Will the dataset be distributed under a license?*
	- Yes, Afrobarometer’s terms of use apply.

5. *Do any export controls or other regulatory restrictions apply?*
	- None.

## **Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Afrobarometer.

2. *How can the owner/curator/manager of the dataset be contacted?*
	- Through Afrobarometer’s official website.

3. *Will the dataset be updated?*
	- Updates occur with each survey round.

4. *Will older versions of the dataset continue to be supported?*
	- Yes, historical datasets remain available.

### 2024-12-03 paper/paper.qmd
datasheet & ethics

@@
 @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.
+@sec-survey-appendix details the survey methodology used in the Afrobaromenter data and @sec-ethics addresses key ethical principles and the ethical challenges of surveying sensitive topics like corruption.
 
@@
 
-## Tareting Education Levels in Anti-Corruption Campaigns {#sec-first-point}
+## Tareting Education Levels in Anti-Corruption Campaigns
 
@@
 
-# Surveys, Sampling, and Observational Data {#sec-survey-appendix}
-
-## Survey Methodolgy and Design
-
-## Sampling Techniques
-
-## Observational Data Challenges
-
-## Proposed Improvements
+# Surveys, Sampling, and Observational Data
+
+## Aforbarometer Methodology Overview and Evaluation {#sec-survey-appendix}
+
+### Overview
+
+Afrobarometer is a  pan-African, non-partisan survey research network established to measure public attitudes on democracy, governance, economic reform, civil society, and quality of like in Africa.
+It relies predominantly on in-person interviews using a standard questionnaire.
+The project covers up to 40 countries in Africa.
+The information collected is intended to be used by various parties including policymakers, activists,teachers and scholars.
+The surveys are conducted using a standardized questionnaire tailored to specific countries through a process called "indigenization", ensuring relevance to local contexts while keeping comparability across nations [@survey_manual_2022].
+
+### Population and sampling frame
+
+The Afrobarometer surveys target all citizens of voting age, typically 18 and above, excluding individuals living in institutions such as prisons, military barracks, or hospitals.
+The sampling frame is based on the most recent official national census.
+When census data is outdated, population estimates or projections are used to ensure relevance.
+The surveys employ a clustered, stratified, multi-stage probability sample design, where:
+
+- Clustered sampling groups respondents geographically to reduce costs and logistical complexity.
+
+- Stratified sampling divides the population into subgroups (e.g., urban/rural or regions) to ensure proportional representation.
+
+- Multi-stage sampling involves multiple rounds of random selection, narrowing down from regions to individual households and respondents.
+
+### Respondent Recruitment
+
+Afrobarometer follows strict protocols to ensure randomness and gender balance during respondent selection.
+Interviewers alternate genders with each new interview, starting each day with the gender opposite to the last interview conducted the previous day.
+If no eligible respondent of the next household.
+Interviews are conducted only after securing informed consent from the respondents, making sure to keep up with ethical guidelines to ensure respect and confidentiality [@survey_manual_2022].
+
+### Smpling Approach
+
+The Probability Proportional to Population Size (PPPS) sampling method makes sure that regions with larger populations have a higher chance of being selected.
+In urban areas, the sampling process typically has four stages: selection of Primary Sampling Units (PSUs) based on population size, random selection of Enumeration Areas (EAs) within PSUs, systemic selection of households within each EA, random selection of respondents within household [@survey_manual_2022].
+In rural areas, an additional stage may be introduced to make sure representativeness across dispersed populations.
+By using PPPS and randomization at every stage, Afrobarometer minimizes biases and makes sure data is collected efficiently [@survey_manual_2022].
+
+### Strengths and Limitations
+
+**Strengths:**
+
+- Random Selection: Ensures every adult citizen has an equal chance of being selected, enhancing representativeness.
+
+- Proportional Sampling: PPPS ensures larger and more populous regions are adequately represented.
+
+- Localized Surveys: Conducted in local languages to ensure accessibility and reduce misinterpretation of questions.
+
+**Limitations:**
+
+- Institutional Exclusion: Citizens in prisons, military barracks, and similar institutions are excluded, potentially overlooking significant perspectives.
+
+- Conflict Zones: Areas affected by conflict or logistical challenges may be excluded, limiting geographic coverage.
+
+- Africa-Wide Generalization: While Afrobarometer provides national-level insights, its findings cannot be generalized to the entire continent due to contextual variations.
+
+## Ethics considerations {#sec-ethics}
+
+### Overview of Afrobarometer’s Ethical Framework
+
+Afrobarometer adheres to  ethical standards to ensure the protection and dignity of survey respondents. Here are the important components of their ethical framework:
+
+- **Informed Consent**: Respondents are provided with detailed information about the survey's purpose, topics, and their rights before participation.
+Verbal consent is obtained to account for literacy variations across surveyed populations [@survey_manual_2022].
+- **Confidentiality and Anonymity**: Personal identifiers are removed during data processing, and data are stored securely to maintain respondent privacy.
+- **Cultural Sensitivity**: Questionnaires are carefully pre-tested and translated into local languages, ensuring they are culturally appropriate and easily understood.
+
+These practices align with established ethical principles in social science research, including those outlined by the World Association for Public Opinion Research [@waporethics].
+
+### Ethical Challenges in Corruption Perception Surveys
+
+Researching perceptions of corruption has unique ethical challenges because of the sensitive and sometimes dangerous nature of corruption:
+
+- **Risks to Respondents**: Respondents may fear repercussions for expressing negative views about governance.
+Afrobarometer mitigates this risk by emphasizing anonymity and employing well-trained enumerators who follow strict protocols [@survey_manual_2022].
+- **Power Dynamics**: Interviewers may inadvertently influence responses due to perceived power imbalances.
+Afrobarometer addresses this by alternating gender in interviews and training enumerators to minimize bias.
+
+### Sampling and Recruitment Ethics
+
+Afrobarometer’s methodology includes a very detailed sampling framework designed to enhance inclusivity and fairness. However, there are still some ethical concerns:
+
+- **Exclusion of Institutional Populations**: Individuals in prisons, military barracks, and similar institutions are excluded, potentially omitting perspectives from disenfranchised groups [@survey_manual_2022].
+- **Gender Quotas**: The enforcement of equal gender representation ensures that women's voices are equally captured, addressing historical disparities in research participation [@survey_manual_2022].
+- **Regional and Security Constraints**: Some areas, particularly conflict zones, may be inaccessible, leading to under representation in survey findings.This is particularly the cause in North-Eastern Nigeria which as a result of criminal groups like Boko Haram, has made it virtually impossible to access that region safely.
+
+### Ethical Data Management and Reporting
+
+Afrobarometer takes significant steps to ensure ethical data handling and dissemination:
+
+- **Data Security**: Survey data are encrypted during storage and transmission, ensuring compliance with data protection regulations.
+- **Transparent Reporting**: Reports explicitly document survey limitations, including regions excluded due to security or logistical challenges.
+- **Avoiding Harm**: Results are contextualized to prevent misinterpretation or harm to surveyed populations. Findings are shared responsibly, avoiding language that could inflame tensions.
+
+### Limitations and Future Ethical Enhancements
+
+Despite its robust framework, Afrobarometer’s approach could be improved in the following areas:
+
+- **Inclusion of Marginalized Populations**: Future iterations could include anonymous digital surveys to capture insights from institutionalized or transient populations.
+- **Addressing Non-Response Bias**: Enhanced recruitment strategies, such as partnerships with community organizations, could increase participation among underrepresented groups.
+- **Community Engagement**: Sharing results directly with communities through accessible formats (e.g., infographics or local town halls) would increase transparency and accountability.
+
+### Conclusion
+
+The ethical considerations underpinning Afrobarometer’s methodology ensure the credibility and validity of its findings while safeguarding respondent dignity.
+However, addressing remaining gaps—such as the exclusion of certain populations and challenges in conflict zones—would further enhance the ethical rigor of corruption perception research in Africa.
+By adhering to established ethical frameworks and remaining responsive to emerging challenges, studies like this can continue to provide valuable insights while maintaining the highest ethical standards.To do my part in ensuring ethical standards are upheld, i have included a datasheet for the Afrobarometer dataset.
 

### 2024-12-03 paper/paper.qmd
Ethical considerations

@@
 ---
-title: "Perceptions of Corruption in Nigeria"
-subtitle: "Rural Nigerians and Less Educated  Groups Report Higher Corruption"
+title: "Shaping Anti-Corruption Campaigns in Nigeria"
+subtitle: "Youth Populations, Urban Areas and Moderately Educated Citizens Are Critical for Anti-Corruption Campaigns "
 author: 

### 2024-12-03 scripts/00-simulate_data.R

@@ -41,7 +41,5 @@ simulated_afrobarometer <-  simulated_afrobarometer %>%
   )
 
 
-#### Simulate data ####
-
 #### Save data ####
 write_csv(simulated_afrobarometer, "data/00-simulated_data/simulated_afrobarometer.csv")

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Tests the structure and validity of the simulated Nigerian Surveys dataset.
 # Author: Fatimah Yunusa
-# Date: 26 September 2024
+# Date: 21 Novemberr 2024
 # Contact: fatimah.yunusa@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 

### 2024-12-03 scripts/02-download_data.R

@@ -9,9 +9,7 @@
 
 
 #### Workspace setup ####
-install.packages("arrow")
-install.packages("tidyverse")
-install.packages("haven")
+
 library(arrow)
 library(tidyverse)
 library(haven)

### 2024-12-03 scripts/03-clean_data.R

@@ -8,10 +8,7 @@
 # Any other information needed? 
 
 #### Workspace setup ####
-install.packages("haven")    
-install.packages("dplyr")    
-install.packages("ggplot2")  
-install.packages("arrow")
+
 library(haven)
 library(dplyr)
 library(ggplot2)

### 2024-12-03 scripts/05-exploratory_data_analysis.R

@@ -10,14 +10,10 @@
 
 #### Workspace setup ####
 
-
-
-#### Exploratory Data Analysis ####
-
-# Load necessary libraries
-install.packages(c("ggplot2", "dplyr"))
 library(ggplot2)
 library(dplyr)
+
+#### Exploratory Data Analysis ####
 
 # Load the cleaned dataset
 cleaned_data <- read_parquet("data/02-analysis_data/fully_cleaned_nigeriasurvey.parquet")
@@ -72,29 +68,22 @@ ggplot(cleaned_data, aes(x = age_group, fill = corruption_presidency)) +
        x = "Age Group",
        y = "Proportion")
 
-# Cross-tabulation of gender and corruption perception
+#  gender and corruption perception
 gender_correlation <- table(cleaned_data$gender, cleaned_data$corruption_presidency)
 print(gender_correlation)
 
-# Cross-tabulation of urban/rural and corruption perception
+#  urban/rural and corruption perception
 urban_rural_correlation <- table(cleaned_data$urban_rural, cleaned_data$corruption_presidency)
 print(urban_rural_correlation)
 
-# Cross-tabulation of education and corruption perception
+#  education and corruption perception
 education_correlation <- table(cleaned_data$education, cleaned_data$corruption_presidency)
 print(education_correlation)
 
-# Correlation between numeric variables (if any)
-# Example: Correlation between age (numeric) and corruption perception (numeric encoding)
+#  Correlation between age (numeric) and corruption perception (numeric encoding)
 cor_age_corruption <- cor(cleaned_data$Q1, as.numeric(cleaned_data$corruption_presidency), use = "complete.obs")
 cat("Correlation between Age and Perception of Corruption:", cor_age_corruption, "\n")
 
-# Save the visualizations
-#ggsave("outputs/eda/corruption_presidency_distribution.png", width = 8, height = 6)
-#ggsave("outputs/eda/education_distribution.png", width = 8, height = 6)
-#ggsave("outputs/eda/corruption_by_education.png", width = 8, height = 6)
-#ggsave("outputs/eda/corruption_by_gender.png", width = 8, height = 6)
-#ggsave("outputs/eda/corruption_by_urban_rural.png", width = 8, height = 6)
-#ggsave("outputs/eda/corruption_by_age_group.png", width = 8, height = 6)
 
-# End of EDA
+
+

### 2024-12-03 scripts/06-model_data.R

@@ -11,21 +11,7 @@
 #### Workspace setup ####
 
 
-### Model data ####
-
-#### Save model ####
-#saveRDS(
-#  first_model,
-#  file = "models/first_model.rds"
-#)
-
-
-# Load necessary libraries
-install.packages("MASS")
-install.packages("dplyr")
-install.packages("modelsummary")
-install.packges("rstanarm")
-linrary(rstanarm)
+library(rstanarm)
 library(MASS)
 library(dplyr)
 library(modelsummary)

### 2024-12-03 paper/paper.qmd
prose checks

--- 2024-12-03 paper/paper.qmd
@@
 ---
-title: "Perceptions of Corruption in Nigeria"
-subtitle: "Rural Nigerians and Less Educated  Groups Report Higher Corruption"
+title: "Shaping Anti-Corruption Campaigns in Nigeria"
+subtitle: "Youth Populations, Urban Areas and Moderately Educated Citizens Are Important for Anti-Corruption Campaigns "
 author: 
@@
 
-#install.packages("modelsummary")
-#install.packages("rstanarm")
-#install.packages("dplyr")
-#install.packages("here")
-#install.packages("arrow")
-#install.packages("tinytable")
 library(modelsummary)
@@
 Making sure outreach efforts are tailored to the unique experiences and perceptions of different demographic groups can increase their effectiveness and increase public trust.
-For example, youth-focused campaigns that leverage social media platforms and urban outreach using investigative journalism can engage the people.
+For example, youth-focused campaigns that use social media platforms and urban outreach using investigative journalism can engage the people.
 At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations.
@@
 @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.
-@sec-survey-appendix details the survey methodology used in the Afrobaromenter data and @sec-ethics addresses key ethical principles and the ethical challenges of surveying sensitive topics like corruption.
+@sec-survey-appendix details the survey methodology used in the Afrobaromenter data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.
 
@@
 that are clear, culturally sensitive, and tailored to elicit meaningful
-responses.
+responses [@Afrobarometer2022codebook].
 
@@
 
-Each survey question acts as a data proxy for these complex real-world
-dynamics, reducing them to quantifiable variables while maintaining
-their conceptual integrity.
-
-This dataset captures a unique moment in Nigeria's socio-political
-landscape, reflecting how citizens perceive democracy and governance in
+Each survey question acts as a data proxy for these real-world
+dynamics, reducing them to quantifiable variables while keeping
+their conceptual integrity.This dataset shows a unique moment in Nigeria's socio-political
+landscape, showing how citizens perceive democracy and governance in
 the context of ongoing economic and political challenges. Alternative
 datasets, such as Nigeria’s national statistics or World Bank survey
-data, could provide economic indicators but lack the granularity of
+data, could provide economic indicators but do not have the granularity of
 Afrobarometer’s public opinion data.
@@
 The data for this study was downloaded, cleaned, analyzed, modeled, and
-visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing valuable survey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies.
+visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies.
 The
@@
 
-#install.packages("knitr")
-#install.packages("kableExtra")
 library(knitr)
@@
 The cleaned dataset used in this study is summarised in
-@tbl-summary-statistics, which provides key statistics to offer an
+@tbl-summary-statistics, which provides important statistics to provide an
 overview of the dataset's structure and characteristics. The most
@@
 categories—"None," "Some," "High," and "All"—with counts for each,
-offering insights into respondents' views on corruption in the
+offering information into respondents' views on corruption in the
 presidency. Additionally, the table details the distribution of
@@
 "Primary," "Secondary," "University," and "Postgraduate." Together,
-these summary statistics provide a comprehensive snapshot of the
+these summary statistics provide a very detailed snapshot of the
 dataset, enabling a clear understanding of its demographic and
@@
 
-The heatmap reveals that respondents who completed secondary school or
+The heatmap shows that respondents who completed secondary school or
 some secondary schooling dominate the High Corruption and Some
@@
 
-The chart reveals that rural and urban respondents share similar
+The chart shows that rural and urban respondents share similar
 patterns of corruption perception. The majority of respondents in both
@@
 
-#install.packages("broom.mixed")
-#install.packages("kableExtra")
-
 library(broom.mixed)
@@
 Higher education levels consistently show positive probabilities,
-indicating that individuals with more advanced education levels are more
+indicating that individuals with higher education levels are more
 likely to perceive higher corruption levels. Living in rural areas has a
@@
 like social media, community-based programs, and public dialogues to
-engage critical urban audiences, while also expanding rural outreach
+engage important urban audiences, while also expanding rural outreach
 through local radio, grassroots organizations, and educational
@@
 between different demographics and seeing how these differences can be
-leveraged to maximize anti corruption campaigns and policy in
+used to maximize anti corruption campaigns and policy in
 Nigeria.From this paper, we find different actionable strategies for
@@
 
-Education also emerges as a key determinant of corruption perceptions.
+Education also emerges as an important determinant of corruption perceptions.
 Secondary school graduates exhibit the highest levels of awareness, this
@@
 Transparent hiring practices, visible enforcement of anti-corruption
-laws, and strengthened whistleblower protections are important steps to
+laws, and strengthened whistle blower protections are important steps to
 showing institutional accountability. Localized outreach through
-community leaders can also help bridge the trust gap, particularly in
+community leaders can also help fix the trust divide, particularly in
 rural settings. Policymakers should put these findings into a
@@
 
-- Africa-Wide Generalization: While Afrobarometer provides national-level insights, its findings cannot be generalized to the entire continent due to contextual variations.
+- Africa-Wide Generalization: While Afrobarometer provides national-level information, its findings cannot be generalized to the entire continent due to contextual variations.
 
@@
 
-- **Inclusion of Marginalized Populations**: Future iterations could include anonymous digital surveys to capture insights from institutionalized or transient populations.
+- **Inclusion of Marginalized Populations**: Future surveys could include anonymous digital surveys to take from institutionalized or transient populations.
 - **Addressing Non-Response Bias**: Enhanced recruitment strategies, such as partnerships with community organizations, could increase participation among underrepresented groups.
@@
 However, addressing remaining gaps—such as the exclusion of certain populations and challenges in conflict zones—would further enhance the ethical rigor of corruption perception research in Africa.
-By adhering to established ethical frameworks and remaining responsive to emerging challenges, studies like this can continue to provide valuable insights while maintaining the highest ethical standards.To do my part in ensuring ethical standards are upheld, i have included a datasheet for the Afrobarometer dataset.
+By adhering to established ethical frameworks and remaining responsive to emerging challenges, studies like this can continue to give important information while maintaining the highest ethical standards.To do my part in ensuring ethical standards are upheld, i have included a datasheet for the Afrobarometer dataset.
 
@@
 
-```{r}
-#| label: fig-variables-of-interest-heatmap
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-#| fig.cap: "combined variables of interest"
-
-#install.packages("tidyr")
-library(tidyr)
-# Combine data for heatmap
-heatmap_data <- cleaned_data %>%
-  pivot_longer(
-    cols = c(URBRUR, corruption_presidency, education, age_group),
-    names_to = "variable",
-    values_to = "category"
-  ) %>%
-  count(variable, category) %>%
-  mutate(variable = factor(variable, levels = c("URBRUR", "corruption_presidency", "education", "age_group")))
-
-# Create heatmap
-ggplot(heatmap_data, aes(x = category, y = variable, fill = n)) +
-  geom_tile(color = "white") +
-  scale_fill_gradient(low = "lightblue", high = "darkblue") +
-  labs(
-    title = "Heatmap of Variable Distributions",
-    x = "Category",
-    y = "Variable",
-    fill = "Count"
-  ) +
-  theme_minimal() +
-  theme(
-    axis.text.x = element_text(angle = 45, hjust = 1)
-  )
-
-```
-
-![Combined plot](combined_plot.png){width="120%"}
+@fig-demo The figure provides an overview of demographic variables and corruption perceptions from the Afrobarometer Nigeria Round 9 survey.
+Rural residents constitute a larger share of the sample, aligning with Nigeria's predominantly rural demographic landscape.
+Corruption perception data shows that "High Corruption" and "Some Corruption" dominate public opinion.
+The education level distribution highlights the prevalence of basic education, with the majority of respondents having completed secondary school.
+Finally, the age distribution indicates that the 25–34 age group is the most represented cohort, suggesting that young adults play a crucial role in shaping perceptions of corruption and governance in Nigeria.
+![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="120%"}
 

### 2024-12-04 paper/paper.qmd
data_diary

@@
 Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions.
-The results show that urban residents and yourger individuals are more likely to perceive high corruption, while rura populations and those with higher education show views that are moderate.
-These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance accountability in Nigeria"
+The results show that urban residents and younger individuals are more likely to perceive high corruption, while rural populations and those with higher education show views that are moderate.
+These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance and accountability in Nigeria"
 format: pdf
@@
 
-Corruption is a very big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth.
+Corruption is a big challenge to governance and development in Nigeria as a result of its ability to undermine public trust and economic growth.
 As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024].
@@
 
-Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways thiis can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context.
-This paper addresses this gap by making these demographics the focus.
+Primarily, this paper is aimed at understanding how different demographic groups perceive corruption in the Nigerian presidency and to identify ways this can help improve anti-corruption campaigns, While existing studies have largely been focused on the institutional dynamics, there seems to be a lack of demographic-specific analysis within the Nigerian context.
+This paper addresses this by making these demographics the focus.
 It does this by using nationally representative data from Afrobarometer [@afrobarometer2023], a leading survey initiative capturing public attitudes on governance, democracy, and corruption across Africa.
@@
 
-Our paper shows that there are alot of disparities in corruption perceptions across demographic groups.
-Younger respondents and urban residents have higher perceptions of corruption, likely because of higer exposure to investigative media and political discourse.
+Our paper shows that there are a lot of disparities in corruption perceptions across demographic groups.
+Younger respondents and urban residents have higher perceptions of corruption, likely because of higher exposure to investigative media and political discourse.
 In contrast, rural populations-often reliant on patronage systems- tend to report more neutral views.
@@
 At the same time, localized, culturally appropriate campaigns in rural areas can address the different needs of these populations.
-A the UNODC emphasizes, 'targeted and effective anti-corruption policies will improve likes of Nigerian citizens" [@afrobarometer2023].
-
-The remainder of this paper is structured as follows; @sec-data detailed the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest.
+As the UNODC emphasizes, "targeted and effective anti-corruption policies will improve lives of Nigerian citizens" [@afrobarometer2023].
+
+The remainder of this paper is structured as follows; @sec-data details the data used for this paper, @sec-model introduces the Bayesian ordinal logistic regression model used to study the relationship between our variables of interest.
 @sec-results presents the findings from the model, detailing how different demographic factors like education and age affect corruption perception in Nigeria.
@@
 @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.
-@sec-survey-appendix details the survey methodology used in the Afrobaromenter data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.
+@sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.@sec-Data-Driven-Narrative-appendix introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.
 
@@
 
-For this analysis, i use the Afrobarometer Round 9, Nigeria, 2023
-survey. Afrobarometer conducts surveys that are nationally
+For this analysis, i use the Afrobarometer Round 9, Nigeria survey. 
+Afrobarometer conducts surveys that are nationally
 representative across African nations to capture public perceptions on
@@
 The data for this study was downloaded, cleaned, analyzed, modeled, and
-visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its code and methodologies.
+visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its methodologies.
 The
@@
     visualization.
--   ***Telling Stories with Data*** [@tellingstories]: This book was
-    referenced for its code and methodologies.
 
@@
 
-# Generate a well-formatted table using kableExtra
+# Generate a table using kableExtra
 kable(
@@
 captures several socioeconomic sentiments within the country.The column
-corruption_presidency captures perceptions of corruption within the
-office of the presidency, derived from responses to the question, “How
+`corruption_presidency` captures perceptions of corruption within the
+office of the presidency, derived from responses to the question, *“How
 many of the following people do you think are involved in corruption, or
 haven’t you heard enough about them to say: the president and officials
-in his office?” The variable education reflects respondents' highest
-level of education completed, gathered from the question, “What is the
-highest level of education you have completed?” The gender variable
+in his office?”* The variable education reflects respondents' highest
+level of education completed, gathered from the question, *“What is the
+highest level of education you have completed?”* The gender variable
 indicates the respondent's gender, collected through direct demographic
 inquiry. The column age_group categorizes respondents into age brackets
-based on the question, “How old are you?” The urban_rural variable
+based on the question,* “How old are you?”* The urban_rural variable
 distinguishes between urban and rural respondents, as recorded by
@@
 #| message: false
-#| tbl-cap: "Detailed Summary Statistics of the Cleaned Dataset"
+#| tbl-cap: "Detailed Summary Statistics of the Cleaned Afrobarometer Dataset"
 
@@
 
-# Ensure the age_group column is a character for correct mapping
+# make sure the age_group column is a character for correct mapping
 cleaned_data <- cleaned_data %>%
@@
 
-# Function to calculate the mode (most frequent category)
+# Function to calculate the mode 
 calculate_mode <- function(x) {
@@
 
-# Adjust line breaks for proper rendering
 line_break <- ifelse(knitr::is_html_output(), "<br>", "\n")
 
-# Prepare the data for the transposed table
+# data for the transposed table
 transposed_summary <- tibble(
@@
 
-# Generate a formatted table
+# formatted table
 kable(
@@
   caption = "Detailed Summary Statistics of the Cleaned Dataset (Transposed)",
-  escape = FALSE # Disables escaping for proper HTML/PDF formatting
+  escape = FALSE 
 ) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) %>%
-  column_spec(2, width = "20em") # Adjust width for better multiline display
+  column_spec(2, width = "20em")
 
@@
 #| message: false
-#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria  in Nigeria"
+#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria"
 
@@
   labs(
-    title = "Relationship between Rural vs. Urban Respondents and Corruption Perceptions",
+    title = " Rural vs. Urban Respondents & Corruption Perceptions",
     x = "Respondent Location",
@@
 respondents within rural and urban groups who hold different corruption
-perceptions.
-
-The chart shows that rural and urban respondents share similar
+perceptions.The chart shows that rural and urban respondents share similar
 patterns of corruption perception. The majority of respondents in both
-groups fall under the Some Corruption and High Corruption categories,
-with Some Corruption being slightly more prevalent. The All Corrupt
+groups fall under the "Some Corruption" and "High Corruption" categories,
+with "Some Corruption" being slightly more prevalent. The "All Corrupt"
 category is the third most common perception in both groups, while the
-No Corruption category is consistently the least represented.
+"No Corruption" category is consistently the least represented.
 
@@
 
-@fig-gender-versus-corruption shows the the relationship between
+@fig-gender-versus-corruption shows the relationship between
 respondents' gender (male and female) and their perceptions of
@@
 the outcome variable, while the Dirichlet prior for $\pi_{ij}$ assumes
-no strong prior preference for any specific corruption category.
-
-The use of these priors provides flexibility for the model while
-preventing overfitting. The posterior distributions for the coefficients
-and thresholds, along with diagnostic checks for model convergence and
-predictive accuracy, can be found in the Appendix.
+no strong prior preference for any specific corruption category.The use of these
+priors provides flexibility for the model while preventing overfitting. The 
+posterior distributions for the coefficients and thresholds, along with 
+diagnostic checks for model convergence and predictive accuracy, can be found in
+the Appendix.
 
@@
 
-# Extract summary
-model_summary <- broom.mixed::tidy(bayesian_model)
-
-# Render as a table
+detailed_model_summary <- broom.mixed::tidy(bayesian_model, conf.int = TRUE, effects = "fixed") %>%
+  select(term, estimate, std.error, conf.low, conf.high)
+
+# Render as a clean table
 knitr::kable(
-  model_summary,
-  caption = "Summary of the Bayesian Model",
-  digits = 2
+  detailed_model_summary,
+  caption = "Detailed Summary of the Bayesian Model with Credible Intervals",
+  digits = 3,
+  col.names = c("Term", "Estimate", "Std. Error", "2.5% CI", "97.5% CI")
 ) %>%
-  kableExtra::kable_styling()
-
-```
-
-The analysis revealed distinct trends in Corruption perceptions in
+  kableExtra::kable_styling(full_width = FALSE) %>%
+  kableExtra::add_header_above(c(" " = 1, "Fixed Effects" = 4))
+```
+
+The analysis revealed trends in corruption perceptions in
 different demographics. Our results are summarized in @tbl-modelresults. 
@@
 Higher education levels(e.g., university or post-graduate
-qualifications) arre associated with positive effects on corruption
+qualifications) are associated with positive effects on corruption
 perceptions, indicating a greater likelihood of perceived higher levels
-of corruption. Begin female shows a small positive association with
+of corruption. Being female shows a small positive association with
 higher corruption perceptions. Residing in rural areas is negatively
 associated with corruption perceptions, suggesting lower perceptions of
-corruption compared to urban counterparts. Agegroups show minimal
+corruption compared to urban counterparts. Age groups show minimal
 variation in their association with corruption perceptions, with no
@@
 
-# Simulating or using your posterior data
+# Loading in posterior data
 predicted_data <- data.frame(
@@
 By looking at these factors, the study aims to inform targeted
-anti-corruption camapigns and policy making. The Bayesian modeling
+anti-corruption campaigns and policy making. The Bayesian modeling
 approach helps us understand the relationship between corruption
@@
 university graduates, report more moderate corruption perceptions, this
-might largely beceause of their exposure to diverse viewpoints and
+might largely be because of their exposure to diverse viewpoints and
 greater access to institutional frameworks that allow for political
@@
 
-## Ethics considerations {#sec-ethics}
+## Ethical considerations {#sec-ethics}
 
@@
 
-These practices align with established ethical principles in social science research, including those outlined by the World Association for Public Opinion Research [@waporethics].
+These practices are aligned with ethical principles in social science research, including those outlined by the World Association for Public Opinion Research [@waporethics].
 
@@
 
+# Amina's Story - A Personal Perspective {#sec-Data-Driven-Narrative-appendix}
+
+Amina is a 25-year-old woman living in Lagos, Nigeria.
+She works long hours at Balogun Market, navigating the daily challenges of urban life.
+She recently completed university, an achievement she’s proud of, and dreams of one day pursuing higher education.
+But like many young Nigerians, Amina often feels frustrated and disillusioned when it comes to governance and corruption.
+
+In conversations with her friends and colleagues, Amina’s voice often reflects anger and disappointment.
+She believes corruption in the presidency is widespread, a sentiment shared by many in her age group and educational background, as revealed in the survey data.
+Growing up in Lagos, where access to news and social media is plentiful, Amina has been exposed to stories of corruption and unfulfilled promises.
+This exposure has shaped her outlook, making her skeptical of government accountability.
+
+Amina’s experiences highlight the role of demographic factors in shaping perceptions of corruption.
+Her youth connects her to a generation that is more vocal about demanding accountability, while her urban residency exposes her to more information about governance.
+At the same time, her level of education gives her the tools to critically analyze these issues, though it also fuels her frustration when systemic problems persist.
+
+Reflecting on Amina’s story reminds us of the ethical responsibility to consider the individuals behind the data.
+Every statistic represents a life, a struggle, and a hope for change.
+By thinking of people like Amina, policymakers and campaigners can design anti-corruption initiatives that genuinely resonate with those they aim to serve.
+Ethical actions begin with understanding these lived realities, ensuring that interventions are meaningful and respectful of the diverse experiences within the population.
+
 # Additional data details
 
-@fig-demo The figure provides an overview of demographic variables and corruption perceptions from the Afrobarometer Nigeria Round 9 survey.
+This figure provides an overview of demographic variables and corruption perceptions from the Afrobarometer Nigeria Round 9 survey.
 Rural residents constitute a larger share of the sample, aligning with Nigeria's predominantly rural demographic landscape.
@@
 The education level distribution highlights the prevalence of basic education, with the majority of respondents having completed secondary school.
-Finally, the age distribution indicates that the 25–34 age group is the most represented cohort, suggesting that young adults play a crucial role in shaping perceptions of corruption and governance in Nigeria.
-![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="120%"}
+Finally, the age distribution indicates that the 25–34 age group is the most represented cohort.
+
+![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="110%"}
 
 # Model details {#sec-model-details}
-
 ## Posterior Predictive Check
-
 ```{r}
@@
 ## Diagnostics
-
 ```{r}

### 2024-12-04 Data_Diary.md.m
datadiary

@@ -1,0 +1,25 @@
+# Data Diary for Corruption Perceptions in Nigeria
+
+This diary documents key steps, decisions, and reflections during the analysis of the Afrobarometer survey data. It provides transparency into the thought process behind data handling and modeling decisions.
+
+## 📊 Data Cleaning
+- **Initial Cleaning:** Missing values were handled using listwise deletion for key variables like corruption perceptions and demographic factors to ensure robust analysis.
+- **Recoding Variables:** Responses were recoded for clarity and consistency (e.g., renaming levels of "corruption_presidency" to "No Corruption," "Some Corruption," etc.).
+- **Urban/Rural Adjustment:** Urban and rural residency categories were reviewed to align with Afrobarometer definitions and national statistics.
+
+## 🔎 Exploratory Analysis
+- **Demographic Trends:** Explored how variables like age, gender, and education influenced corruption perceptions, which helped refine the focus of the analysis.
+- **Outlier Detection:** Identified outliers in age and education data, confirming their validity before inclusion in the model.
+
+## 📐 Modeling Decisions
+- **Bayesian Ordinal Logistic Regression:** Chosen for its ability to handle ordered categorical outcomes while incorporating prior information about the relationships between variables.
+- **Model Validation:** Posterior predictive checks were used to ensure the model accurately captured observed data patterns.
+
+## 🤔 Ethical Considerations
+- **Data Anonymity:** Ensured no personally identifiable information (PII) was included or inferred from the dataset.
+- **Bias Awareness:** Considered the potential biases introduced by survey design and non-response, emphasizing these in the Ethics section of the paper.
+
+## 📜 Important Lessons Learned
+- Demographics play a significant role in shaping perceptions of corruption, which provides valuable insights for targeted anti-corruption campaigns.
+- Careful attention to sampling frames and data preprocessing is essential for reliable and meaningful analysis.
+

### 2024-12-04 paper/paper.qmd
final edits!!

@@
 @sec-model-details shows plots for Posterior predictive checks and Diagnostics as well as their analysis.
-@sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.@sec-Data-Driven-Narrative-appendix introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.
+@sec-survey-appendix details the survey methodology used in the Afrobarometer data and @sec-ethics addresses very important ethical principles and the ethical challenges of surveying sensitive topics like corruption.
+@sec-narrative introduces a narrative example, 'Amina's Story,' to humanize the data by showing how demographic factors like age, education, and urban residency shape individual perceptions of corruption, while emphasizing the ethical importance of considering the lived experiences behind the data.
 
@@
 
-# Amina's Story - A Personal Perspective {#sec-Data-Driven-Narrative-appendix}
+# Amina's Story - A Personal Perspective {#sec-narrative}
 

### 2024-12-04 scripts/02-download_data.R
Update 02-download_data.R

@@ -15,8 +15,6 @@ library(tidyverse)
 library(haven)
 
 
-# Import the .sav file
-nigeriasurvey <- read_sav("~/Downloads/nigeriasurvey.sav")
 
 # View the imported data (optional)
 View(nigeriasurvey)

### 2024-12-04 scripts/03-clean_data.R
Update 03-clean_data.R

@@ -14,7 +14,6 @@ library(dplyr)
 library(ggplot2)
 library(arrow)
 
-nigeriasurvey <- read_sav("~/Downloads/nigeriasurvey.sav")
 
 # Save the raw data as a Parquet file 
 write_parquet(nigeriasurvey, "data/01-raw_data/nigeriasurvey.parquet")

### 2024-12-22 paper/paper.qmd
final edits
final typos fixed!

@@
   - Fatimah Yunusa
-thanks: "Code and data are available at:https://github.com/fatimahsy/Nigeria_Democracy-"
+thanks: "Code and data are available at: [https://github.com/fatimahsy/Nigeria_Democracy-/tree/main](https://github.com/fatimahsy/Nigeria_Democracy-/tree/main)"
 date: today
 date-format: long
-abstract: "Peceptions of corruption in the Nigerian presidency vary significantly across demogrpahic groups.
-Using Afrobarometer survey data and Bayesisan ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions.
+abstract: "Perceptions of corruption in the Nigerian presidency vary significantly across demographic groups.
+Using Afrobarometer survey data and Bayesian ordinal logistic regression, this study looks at how education, gender, age, and urban versus rural residence influence these perceptions.
 The results show that urban residents and younger individuals are more likely to perceive high corruption, while rural populations and those with higher education show views that are moderate.
-These results show the need for targeted anti-corruption campaigns to adress demographic differences and imporve governance and accountability in Nigeria"
+These results show the need for targeted anti-corruption campaigns to address demographic differences and improve governance and accountability in Nigeria"
 format: pdf
@@
 As the United Nations Office on Drugs and Crime (UNODC) stated, "corruption affects the lives of ordinary Nigerian, impeding development and eroding public trust in institutions [@corruptionsurvey2024].
-This paper looks into the role of demographic factors-education,gender,age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.
+This paper looks into the role of demographic factors-education, gender, age, and urban versus rural residence-in shaping perceptions of corruption in the Nigerian presidency.
 
@@
 actionable lintel. The Afrobarometer survey translates these real world
-perceptions into quantifiable data using survey instruments.The process
+perceptions into quantifiable data using survey instruments. The process
 begins with identifying relevant phenomena in the Nigerian
@@
 dynamics, reducing them to quantifiable variables while keeping
-their conceptual integrity.This dataset shows a unique moment in Nigeria's socio-political
+their conceptual integrity. This dataset shows a unique moment in Nigeria's socio-political
 landscape, showing how citizens perceive democracy and governance in
@@
 The data for this study was downloaded, cleaned, analyzed, modeled, and
-visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing importantsurvey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its methodologies.
+visualized using R [@citeR], a statistical programming language.[@afrobarometer2023] served as the primary data source, providing important survey data for analysis.***Telling Stories with Data*** [@tellingstories] was referenced for its methodologies.
 The
@@
 Afrobarometer Round 9 Nigeria Survey [@afrobarometer2023], which
-captures several socioeconomic sentiments within the country.The column
+captures several socioeconomic sentiments within the country. The column
 `corruption_presidency` captures perceptions of corruption within the
@@
 #| message: false
-#| fig.cap: "Relationship between Education Levels and corruption percetpions in Nigeria"
+#| fig.cap: "Relationship between Education Levels and corruption perceptions in Nigeria"
 
@@
 only informal education are sparsely represented across all
-categories.There is a notable concentration of corruption perceptions
+categories. There is a notable concentration of corruption perceptions
 among respondents with mid-level education (secondary schooling), while
@@
 contrast, younger respondents (18–24) and older respondents (55+) report
-lower levels of corruption perception in these categories.In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts. The No
+lower levels of corruption perception in these categories. In the All Corrupt category, the 25–34, 35–44, and 55+ age groups dominate, while the 18–24 and 45–54 groups have lower counts. The No
 Corruption category has low counts across all age groups, indicating
@@
 respondents within rural and urban groups who hold different corruption
-perceptions.The chart shows that rural and urban respondents share similar
+perceptions. The chart shows that rural and urban respondents share similar
 patterns of corruption perception. The majority of respondents in both
@@
 the outcome variable, while the Dirichlet prior for $\pi_{ij}$ assumes
-no strong prior preference for any specific corruption category.The use of these
+no strong prior preference for any specific corruption category. The use of these
 priors provides flexibility for the model while preventing overfitting. The 
@@
 ordered levels. The table includes predictors such as education level,
-gender, urban or rural location, and agre group, which are modeled to
+gender, urban or rural location, and age group, which are modeled to
 explain variations in corruption perceptions. Each predictor's
@@
 
-Higher education levels(e.g., university or post-graduate
+Higher education levels (e.g., university or post-graduate
 qualifications) are associated with positive effects on corruption
@@
 
-## Tareting Education Levels in Anti-Corruption Campaigns
+## Targeting Education Levels in Anti-Corruption Campaigns
 
@@
 used to maximize anti corruption campaigns and policy in
-Nigeria.From this paper, we find different actionable strategies for
+Nigeria. From this paper, we find different actionable strategies for
 improving the effectiveness of anti-corruption campaigns in Nigeria.
@@
 education into school curricula could early awareness and long-term
-attitudinal changes.Youth engagement is very important, given that
+attitudinal changes. Youth engagement is very important, given that
 younger age groups, particularly those aged 25–34, report the highest
@@
 within these urban rural classifications, which could change the
-understanding of corruption perceptions further.The last limitation is
-with the bayesian model, because while the Bayesian model accounts for
+understanding of corruption perceptions further. The last limitation is
+with the Bayesian model, because while the Bayesian model accounts for
 uncertainty, it does not address potential unobserved variables, like
@@
 
-## Aforbarometer Methodology Overview and Evaluation {#sec-survey-appendix}
+## Afrobarometer Methodology Overview and Evaluation {#sec-survey-appendix}
 
@@
 The project covers up to 40 countries in Africa.
-The information collected is intended to be used by various parties including policymakers, activists,teachers and scholars.
+The information collected is intended to be used by various parties including policymakers, activists, teachers and scholars.
 The surveys are conducted using a standardized questionnaire tailored to specific countries through a process called "indigenization", ensuring relevance to local contexts while keeping comparability across nations [@survey_manual_2022].
@@
 
-### Smpling Approach
+### Sampling Approach
 
@@
 - **Gender Quotas**: The enforcement of equal gender representation ensures that women's voices are equally captured, addressing historical disparities in research participation [@survey_manual_2022].
-- **Regional and Security Constraints**: Some areas, particularly conflict zones, may be inaccessible, leading to under representation in survey findings.This is particularly the cause in North-Eastern Nigeria which as a result of criminal groups like Boko Haram, has made it virtually impossible to access that region safely.
+- **Regional and Security Constraints**: Some areas, particularly conflict zones, may be inaccessible, leading to under representation in survey findings.
+This is particularly the cause in North-Eastern Nigeria which as a result of criminal groups like Boko Haram, has made it virtually impossible to access that region safely.
 
@@
 However, addressing remaining gaps—such as the exclusion of certain populations and challenges in conflict zones—would further enhance the ethical rigor of corruption perception research in Africa.
-By adhering to established ethical frameworks and remaining responsive to emerging challenges, studies like this can continue to give important information while maintaining the highest ethical standards.To do my part in ensuring ethical standards are upheld, i have included a datasheet for the Afrobarometer dataset.
+By adhering to established ethical frameworks and remaining responsive to emerging challenges, studies like this can continue to give important information while maintaining the highest ethical standards.
+To do my part in ensuring ethical standards are upheld, i have included a datasheet for the Afrobarometer dataset.
 
@@
 Finally, the age distribution indicates that the 25–34 age group is the most represented cohort.
-
 ![Demographic Distributions of the Afrobarometer Data](combined_plot.png){#fig-demo width="110%"}
